---
title: "EFiT DAG models"
output:
  word_document: default
  html_notebook: default
  pdf_document: default
editor_options:
  chunk_output_type: inline
---
```{r load packages, echo=FALSE, warning=FALSE, message=FALSE}
library(dagitty, warn.conflicts=F, quietly=T)
library(ggdag, warn.conflicts=F, quietly=T)
library(tidyverse,warn.conflicts=F, quietly=T)
```

```{r simple dag function, echo = FALSE}
gg_simple_dag <- function(d) {
  
  d %>% 
    ggplot(aes(x = x, y = y, xend = xend, yend = yend)) +
    geom_dag_point(color = "steelblue", alpha = 1/2, size = 12) +
    geom_dag_text(color = "black") +
    geom_dag_edges() + 
    theme_dag()
  
}
```
```{r fancy dag function, echo = FALSE}

gg_fancy_dag <- function(d, x = 1, y = 1, circle = "U") {
  
  d %>% 
    ggplot(aes(x = x, y = y, xend = xend, yend = yend)) +
    geom_dag_point(aes(color = name == circle),
                   alpha = 1/2, size = 12, show.legend = F) +
    geom_point(x = x, y = y, 
               size = 6.5, shape = 1, stroke = 1, color = "orange") +
    geom_dag_text(color = "black") +
    geom_dag_edges() + 
    scale_color_manual(values = c("steelblue", "orange")) +
    theme_dag()
  
}
```

```{r simple assocation model, echo = FALSE}
group_m1 <- dagify(Ef ~~ T_h)

group_m1 %>%  ggplot(aes(x = x, y = y, xend = xend, yend = yend)) +
    geom_dag_point(color = "steelblue", alpha = 1/2, size = 12) +
    geom_dag_text(color = "black") +
    geom_dag_edges(curvature = 0) + 
    theme_dag()
```

```{r association model with confounders, echo = FALSE}
# Initialize the DAG. "y ~ x" means that x is a parent of y (y <- x)
group_m2 <- dagify(
  T_h ~~ Ef, 
  T_h ~~ Age + H_t + Dep + Anx + Str
  ) 

# Plot the DAG
group_m2 %>% ggplot(aes(x = x, y = y, xend = xend, yend = yend)) +
    geom_dag_point(color = "steelblue", alpha = 1/2, size = 12) +
    geom_dag_text(color = "black") +
    geom_dag_edges(curvature = 0) + 
    theme_dag()
```

#Full models

##full1

```{r v1, echo=FALSE, eval=TRUE}
dg <- downloadGraph(x = "dagitty.net/mkmvQwy")

#TEF_v1 <- tidy_dagitty(dg)

plot(dg)
#rdag <- TEF_v1 %>% ggdag_classic(size = 4) +
  #theme_dag()

#TEF_v1 %>% ggdag() +theme_dag_blank()

#TEF_v1 %>% gg_fancy_dag(x = 10, y = 10, circle = "Ef")

```

**Variable key**

* Age = age
* C_f = self-perception of cognitive failures
* C_r = cognitive reserve
* Dis = psychological distress
* Ef = executive function
* Gen = gender
* H_h = hearing handicap
* H_t = hearing thresholds
* T_d = tinnitus duration
* T_h = tinnitus handicap
* T_l = tinnitus laterality
* T_p = tinnitus presence
* Rum = rumination

The SCM presented here represents my assumptions regarding the relationship between cognitive performance and tinnitus distress. The primary theoretical claim is that tinnitus distress is partly caused by latent executive abilities (Ef -> T_h). 
The other components of the model are specified based on 1) logical causal relationships, 2) insights from research in this thesis, and 3) theoretical interrelations informed by the wider literature. 

1. Logical causal relationships: these are primarily nodes on the periphery of the model and include relationships between age, cognition, and hearing thresholds. For example, while there is a well known association between age and hearing thresholds, the causal relationship can be confidently specified with a unidirectional arrow (Age -> H_t) because hearing thresholds can never be the cause of a person's chronological age. Similarly, an individual's level of tinnitus distress cannot cause their gender, duration of tinnitus, or perceived tinnitus laterality. 

The model is agnostic about many plausible but uncertain causal relationship (e.g. tinnitus distress and global psychological distress).

2. Thesis insights: various nodes have been included due to their demonstrated association with tinnitus distress in previous sections of this thesis. Clarke et al. (REF) demonstrated an association between executive functioning and tinnitus distress through meta-analysis. This model suggests a causal relationship, with executive abilities causing tinnitus distress (see EF -> T model section). Clarke et al. (REF) also demonstrated an association between tinnitus distress and self-perceived cognitive failures.The EFiT study presented in Chapter 4 also demonstrated verified this assocation. The study found an association between CFQ and EF?

3. Theoretical interrelations: relationships between various nodes are presumed and/or supported from the wider literature. Rumination and executive function (REF)

Using this model  we can get the estimated effect of Ef on tinnitus handicap. The minimum adjustment set for this model is:

```{r v1 adjustment sets, echo = FALSE, eval = TRUE}
adjustmentSets(dg, 
               exposure = "Ef", 
               outcome = "T_h")

adjustmentSets(dg, 
               exposure = "Dis", 
               outcome = "Ef")
```

```{r v2, echo = FALSE}
dg2 <- downloadGraph("dagitty.net/mvHFye4 ")
plot(dg2)
```

This is full1 with tinnitus loudness of tinnitus added to the model. The minimum adjustment set for this model is:

```{r v2 adjustment sets, echo = FALSE, eval = TRUE}
adjustmentSets(dg2, 
               exposure = "Ef", 
               outcome = "T_h")
```

#Overlap models

This is the overlapping part of the full model, testable between the Bothersome Tinnitus and  Tinnitus groups in both datasets with the however there are some general caveats and points of interest:

Global psychological distress is measured by the DASS21 in EFiT and Core-OM in thesis data. There does not appear to be any literature that directly compares the correlation between the two, so this is an assumption that the summation of both questionnaires gets at global psychological distress.

Cognitive failures (C_f) is measured by CFQ in EFiT and TFI-C in thesis data.

```{r overlap1, echo = FALSE, eval = TRUE}
dg3 <- downloadGraph("dagitty.net/mBGN2IQ")
plot(dg3)
```

The minimum adjustment set for this model is:
```{r overlap1 adjustment set, echo = FALSE, eval=TRUE}
adjustmentSets(dg3, 
               exposure = "Ef", 
               outcome = "T_h")
```

This model does not feature rumination so the estimate will be confounded in thesis data compared to the full model.