---
title: "EFiT Data Analysis"
author: "N. A. Clarke"
date: "06 March 2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, results = FALSE )
```

```{r load packages}
library(broom)
library(effectsize)
library(rstanarm)
library(bayestestR)
library(see)
library(insight)
library(bayesplot)
library(psych)
library(skimr)
library(cowplot)
library(viridis)
library(ggdag)
library(readxl)
library(tidyverse)
library(bayesplot)
library(tidybayes)
```

```{r load in data file and tidy, warning=FALSE}
efit <- read_xlsx("EFiT_Main data set_5MARCH2020.xlsx") %>% 
  filter(!partNum == 3, !partNum ==30, !partNum == 79) #remove participants no.3 failed screen, no.30 had to withdraw, no.79 may have unreliable results 
#select varibles that aren't automatically processed with other scripts
efit <- efit %>% select(partNum:dualTask_wordsDiff, matrixReason, keepTrack)
efit <- efit %>% rename(participant = partNum)
#load files for automatically processed scripts: dual, nls, rif, rule, stroop
stroopJoin <- read_csv("processedStroop.csv")
ruleJoin <- read_csv("processedRule.csv") 
nlsJoin <- read_csv("processedNLS.csv")
dualJoin <- read_csv("processedDual.csv")
rifJoin <- read_csv("processedRIF.csv")
#join to main set by participant number
efit <- left_join(efit, ruleJoin, by = "participant")#join rule file
efit <- left_join(efit, stroopJoin, by = "participant")#join stroop file
efit <- left_join(efit, nlsJoin, by = "participant")#join nls file
efit <- left_join(efit, dualJoin, by = "participant")#join dual file
efit <- left_join(efit, rifJoin, by = "participant")#join rif file
```
#Data overview and descriptive statistics
```{r create new variables}
efit <- efit %>% 
  mutate(
    THI_cat = ifelse(
      THI >= 38 ,"bothersome tinnitus", ifelse(
        THI > 0 & THI <= 37, "tinnitus", "control"
      ))) #add a categorical variable with the groups split by THI scores

efit$THI_cat <- as.factor(efit$THI_cat) %>% ordered(levels = c("control", "tinnitus", "bothersome tinnitus"))#factorise tinnitus groups

#divide CRIq score by age
efit <- efit %>% mutate(CRIq_aged = CRIq/age)

#multiply DASS subscale scores by 2 and create DASS total variable
efit <- efit %>% 
  mutate(DASS_D = DASS_D*2,
         DASS_A = DASS_A*2,
         DASS_S = DASS_S*2,
         DASS_total = DASS_D+DASS_A+DASS_S)

#create new categorical variables for DASS_D subscale
efit <- efit %>% 
  mutate(
    DASS_D_cat = ifelse(
      DASS_D >= 28 ,"extremely severe", ifelse(
        DASS_D >= 21 & DASS_D <= 27, "severe", ifelse(
          DASS_D >= 14 & DASS_D <= 20, "moderate", ifelse(
          DASS_D >= 10 & DASS_D <= 13, "mild", "normal"
          )
        )
      ))) 

#create new categorical variables for DASS_A subscale
efit <- efit %>% 
  mutate(
    DASS_A_cat = ifelse(
      DASS_A >= 20 ,"extremely severe", ifelse(
        DASS_A >= 15 & DASS_A <= 19, "severe", ifelse(
          DASS_A >= 10 & DASS_A <= 14, "moderate", ifelse(
          DASS_A >= 8 & DASS_A <= 9, "mild", "normal"
          )
        )
      ))) 

#create new categorical variables for DASS_S subscale
efit <- efit %>% 
  mutate(
    DASS_S_cat = ifelse(
      DASS_S >= 34 ,"extremely severe", ifelse(
        DASS_S >= 26 & DASS_S <= 33, "severe", ifelse(
          DASS_S >= 19 & DASS_S <= 25, "moderate", ifelse(
          DASS_S >= 15 & DASS_S <= 18, "mild", "normal"
          )
        )
      ))) 
#factorise DASS subscale categories groups
efit$DASS_D_cat <- as.factor(efit$DASS_D_cat) %>% ordered(levels = c("normal", "mild", "moderate", "severe", "extremely severe"))

efit$DASS_A_cat <- as.factor(efit$DASS_A_cat) %>% ordered(levels = c("normal", "mild", "moderate", "severe", "extremely severe"))

efit$DASS_S_cat <- as.factor(efit$DASS_S_cat) %>% ordered(levels = c("normal", "mild", "moderate", "severe", "extremely severe"))

#create new RIF variable (proportion of correct respones and RIFdif (i.e. a measure of the RIF effect)
efit <- efit %>% 
mutate(pRIF_RpPlus = (Rp_plus/12) * 100, 
       pRIF_RpMinus = (Rp_minus/12) * 100,
       pRIF_Np = (Np/24) * 100,
       pRIF_total = ((Rp_plus + Rp_minus + Np)/48) * 100,
       RIF_Diff = pRIF_Np - pRIF_RpMinus)

opts <- options()  # save old colour options
#set new colour options
options(ggplot2.continuous.colour="viridis")
options(ggplot2.continuous.fill = "viridis")

```
##Group counts
```{r tinnitus group demographics}
#group_by tinnitus groups for mean demographics and self-report measures
group_descriptive_table <- efit %>% 
  group_by(THI_cat) %>% 
  summarise(group_count = n(),
            mean_age = mean(age),
            age_sd = sd(age),
            median_age = median(age),
            mean_hearing_threshold = mean(hearThresh),
            hearing_threshold_sd = sd(hearThresh),
            mean_CFQ = mean(CFQ),
            CFQ_sd = sd(CFQ),
            mean_RRS = mean(RRS),
            RRS_sd = sd(RRS),
            mean_CRIq = mean(CRIq),
            CRIq_sd = sd(CRIq),
            mean_DASS_D = mean(DASS_D),
            mean_CRIq_aged = mean(CRIq_aged),
            CRIq_aged_sd = sd(CRIq_aged),
            DASS_D_sd = sd(DASS_D),
            mean_DASS_A = mean(DASS_A),
            DASS_A_sd = sd(DASS_A),
            mean_DASS_S = mean(DASS_S),
            DASS_S_sd = sd(DASS_S))

group_descriptive_table <- t(group_descriptive_table)

group_descriptive_table <- as.data.frame(group_descriptive_table)

names(group_descriptive_table) <- c("control", "tinnitus", "bothersome tinnitus")

group_descriptive_table <- group_descriptive_table[-1,]

group_descriptive_table$control <- as.character(group_descriptive_table$control)#covert from factor to character before numeric
group_descriptive_table$control <- as.numeric(group_descriptive_table$control)
group_descriptive_table$control <- signif(group_descriptive_table$control,2)

group_descriptive_table$tinnitus <- as.character(group_descriptive_table$tinnitus)#covert from factor to character before numeric
group_descriptive_table$tinnitus <- as.numeric(group_descriptive_table$tinnitus)
group_descriptive_table$tinnitus <- round(group_descriptive_table$tinnitus,2)

group_descriptive_table$`bothersome tinnitus` <- as.character(group_descriptive_table$`bothersome tinnitus`)#covert from factor to character before numeric
group_descriptive_table$`bothersome tinnitus` <- as.numeric(group_descriptive_table$`bothersome tinnitus`)
group_descriptive_table$`bothersome tinnitus` <- round(group_descriptive_table$`bothersome tinnitus`,2)

```
table group descriptives
`r knitr::kable(group_descriptive_table)`
#
```{r cog measures mean and SD table}
cog_descriptives <- efit %>% 
  group_by(THI_cat) %>% 
  summarise(mean_dual_words_easy = mean(dualTask_wordsEasy),
         dual_words_easy_sd = sd (dualTask_wordsEasy),
         mean_dual_words_hard = mean(dualTask_wordsDiff),
         dual_words_hard_sd = sd(dualTask_wordsDiff),
         mean_dual_numbers = mean(dual_task_total),
         dual_numbers_sd = sd(dual_task_total),
         mean_matrix = mean(matrixReason),
         matrix_sd = sd(matrixReason),
         mean_keep_track = mean(keepTrack),
         keep_track_sd = sd(keepTrack),
         mean_switch_trials = mean(switch_trials),
         switch_trials_sd = sd(switch_trials),
         mean_none_switch_trials = mean(none_switch_trials),
         none_switch_trials_sd = sd(none_switch_trials),
         mean_switch_cost = mean(switch_cost),
         switch_cost_sd = sd(switch_cost),
         mean_switch_error = mean(rule_errors),
         switch_errors_sd = sd(rule_errors),
         mean_stroop_congruent = mean(stroop_congruent),
         stroop_congruent_sd = sd(stroop_congruent),
         mean_stroop_incongruent = mean(stroop_incongruent),
         stroop_incongruent_sd = sd(stroop_incongruent),
         mean_stroop_neutral = mean(stroop_neutral),
         stroop_neutral_sd = sd(stroop_neutral),
         mean_stroop_errors = mean(stroop_errors),
         stroop_errors_sd = sd(stroop_errors),
         mean_nls_correct = mean(nls_correct),
         nls_correct_sd = sd(nls_correct),
         mean_pRIF_RpPlus = mean(pRIF_RpPlus),
         pRIF_RpPlus_sd = sd(pRIF_RpPlus),
         mean_pRIF_RpMinus = mean(pRIF_RpMinus),
         pRIF_RpMinus_sd = sd(pRIF_RpMinus),
         mean_pRIF_Np = mean(pRIF_Np),
         pRIF_Np_sd = sd(pRIF_Np),
         mean_RIF_diff = mean(RIF_Diff),
         RIF_diff_sd = sd(RIF_Diff),
         mean_pRIF_total = mean(pRIF_total),
         pRIF_total_sd = sd(pRIF_total)
  )

cog_descriptives <- t(cog_descriptives)

cog_descriptives <- as.data.frame(cog_descriptives)

names(cog_descriptives) <- c("control", "tinnitus", "bothersome tinnitus")

cog_descriptives <- cog_descriptives[-1,]

cog_descriptives$control <- as.character(cog_descriptives$control)#covert from factor to character before numeric
cog_descriptives$control <- as.numeric(cog_descriptives$control)
cog_descriptives$control <- round(cog_descriptives$control,2)

cog_descriptives$tinnitus <- as.character(cog_descriptives$tinnitus)#covert from factor to character before numeric
cog_descriptives$tinnitus <- as.numeric(cog_descriptives$tinnitus)
cog_descriptives$tinnitus <- round(cog_descriptives$tinnitus,2)

cog_descriptives$`bothersome tinnitus` <- as.character(cog_descriptives$`bothersome tinnitus`)#covert from factor to character before numeric
cog_descriptives$`bothersome tinnitus` <- as.numeric(cog_descriptives$`bothersome tinnitus`)
cog_descriptives$`bothersome tinnitus` <- round(cog_descriptives$`bothersome tinnitus`,2)
```
table cog descriptives 
`r knitr::kable(cog_descriptives)`

##Histograms
```{r historgram age,eval= F}
age_histo <- efit %>% ggplot(aes(x = age)) +
  geom_histogram(bins = 35) +
  facet_grid(. ~ THI_cat) +
  theme_cowplot() +
  theme(strip.text.x = element_text(size=10))

ggsave("age_histograms.tiff",plot = age_histo, units="in", width=5, height=4, dpi=400, compression = 'lzw')
```

```{r historgram hearing, eval = F}
efit %>% ggplot(aes(x = hearThresh)) +
  geom_histogram() +
  facet_grid(. ~ THI_cat) +
  theme_cowplot()
```
##DASS stacked bar charts
```{r depression stacked bar chart, eval = F}
DASS_D_stacked <- ggplot(data=efit, 
       aes(x = THI_cat, fill = fct_rev(DASS_D_cat))) +
  geom_bar(position = "fill") +
  scale_y_continuous(breaks = c(0,.1,.2,.3,.4,.5,.6,.7,.8,.9,1)) +
  xlab("group") +
  ylab("proportion") +
  labs(fill = "DASS Category") +
  ggtitle("Proportion of Depression Scores by Group") +
  theme_cowplot() +
  theme(plot.title = element_text(size = 14),
        legend.text=element_text(size=10),
        legend.title =element_text(size=11, face = "bold"),
        panel.grid.major.y = element_line(colour = "light gray", linetype = "dashed"), 
        axis.text.x.bottom = element_text(size = 8))

ggsave("DASS_D_stacked_prop.tiff",plot = DASS_D_stacked, units="in", width=5, height=4, dpi=400, compression = 'lzw')
```

```{r stress stacked bar chart, eval = F}
DASS_S_stacked <- ggplot(data=efit, 
       aes(x = THI_cat, fill = fct_rev(DASS_S_cat))) +
  geom_bar(position = "fill") +
  scale_y_continuous(breaks = c(0,.1,.2,.3,.4,.5,.6,.7,.8,.9,1)) +
  xlab("group") +
  ylab("proportion") +
  labs(fill = "DASS Category") +
  ggtitle("Proportion of Stress Scores by Group") +
  theme_cowplot() +
  theme(plot.title = element_text(size = 14),
        legend.text=element_text(size=10),
        legend.title =element_text(size=11, face = "bold"),
        panel.grid.major.y = element_line(colour = "light gray", linetype = "dashed"), 
        axis.text.x.bottom = element_text(size = 8))

ggsave("DASS_S_stacked_prop.tiff",plot = DASS_S_stacked, units="in", width=5, height=4, dpi=400, compression = 'lzw')
```

```{r anxiety stacked bar chart, eval = F}
DASS_A_stacked <- ggplot(data=efit, 
       aes(x = THI_cat, fill = fct_rev(DASS_A_cat))) +
  geom_bar(position = "fill") +
  scale_y_continuous(breaks = c(0,.1,.2,.3,.4,.5,.6,.7,.8,.9,1)) +
  xlab("group") +
  ylab("proportion") +
  labs(fill = "DASS Category") +
  ggtitle("Proportion of Anxiety Scores by Group") +
  theme_cowplot() +
  theme(plot.title = element_text(size = 14),
        legend.text=element_text(size=10),
        legend.title =element_text(size=11, face = "bold"),
        panel.grid.major.y = element_line(colour = "light gray", linetype = "dashed"), 
        axis.text.x.bottom = element_text(size = 8))

ggsave("DASS_A_stacked_prop.tiff",plot = DASS_A_stacked, units="in", width=5, height=4, dpi=400, compression = 'lzw')
```

```{r create variable for DASS subscale scores}
mod_DASS <- efit %>% 
  mutate(mod_DASS = ifelse(DASS_D > 13 |
                             DASS_A > 9 |
                             DASS_S > 18, "moderate or higher", "normal or mild"))

mod_DASS %>% select(DASS_D_cat, DASS_A_cat, DASS_S_cat, mod_DASS)
```

```{r moderate DASS scores stacked bar chart, eval = F}
mod_DASS_plot <- ggplot(data=mod_DASS, 
       aes(x = THI_cat, fill = fct_rev(mod_DASS))) +
  geom_bar(position = "fill") +
  scale_y_continuous(breaks = c(0,.1,.2,.3,.4,.5,.6,.7,.8,.9,1)) +
  xlab("group") +
  ylab("proportion") +
  labs(fill = "DASS Category") +
  ggtitle("Proportion of Moderate or Higher \nDepression, Anxiety, or Stress by Group") +
  theme_cowplot() +
  theme(plot.title = element_text(size = 12),
        legend.text=element_text(size=10),
        legend.title =element_text(size=11, face = "bold"),
        panel.grid.major.y = element_line(colour = "light gray", linetype = "dashed"), 
        axis.text.x.bottom = element_text(size = 8)) +
  scale_fill_viridis_d()

ggsave("mod_DASS_stacked_prop.tiff",plot = mod_DASS_plot, units="in", width=5, height=4, dpi=400, compression = 'lzw')
```

#T-tests
```{r filtered data frames of different groups}
#filter by groups for statistical tests
controls <- efit %>% 
  filter(THI_cat == "control")
mild_tin <- efit %>% 
  filter(THI_cat == "tinnitus")
modsev_tin <- efit %>% 
  filter(THI_cat == "bothersome tinnitus")
```
##Controls and Mild
###Number-letter sequencing
```{r t-test control-mild letter-number sequencing}
nls_control_mild_t.test <- t.test(controls$nls_correct, mild_tin$nls_correct, alternative = "greater",var.equal = F)#controls greater than mild

```

```{r tidy control-mild letter-number sequencing t-test to extract coefficients}
nls_control_mild_t.test_tidy <- tidy(nls_control_mild_t.test)

nls_control_mild_t.test_tidy <- nls_control_mild_t.test_tidy %>% 
  mutate(task = "number_letter_sequencing", groups = "control_mild")
```

###Keep-track
```{r t-test control-mild keep-track}
keeptrack_control_mild_t.test <- t.test(controls$keepTrack, mild_tin$keepTrack, alternative = "greater",var.equal = F)#controls greater than mild
```

```{r tidy control-mild keep-track t-test to extract coefficients}
keeptrack_control_mild_t.test_tidy <- tidy(keeptrack_control_mild_t.test)

keeptrack_control_mild_t.test_tidy <- keeptrack_control_mild_t.test_tidy %>% 
  mutate(task = "keeptrack", groups = "control_mild")
```

###Stroop
####Response time (incongruent)
```{r t-test control-mild stroop}
stroopRT_control_mild_t.test <- t.test(controls$stroop_incongruent, mild_tin$stroop_incongruent, alternative = "less",var.equal = F)#controls less than mild
```

```{r tidy control-mild stroop t-test to extract coefficients}
stroopRT_control_mild_t.test_tidy <- tidy(stroopRT_control_mild_t.test)

stroopRT_control_mild_t.test_tidy <- stroopRT_control_mild_t.test_tidy %>% 
  mutate(task = "stroop_rt", groups = "control_mild")
```

####Errors
```{r t-test control-mild stroop errors}
stroopErr_control_mild_t.test <- t.test(controls$stroop_errors, mild_tin$stroop_errors, alternative = "less",var.equal = F)#controls less than mild
```

```{r tidy control-mild stroop errors t-test to extract coefficients}
stroopErr_control_mild_t.test_tidy <- tidy(stroopErr_control_mild_t.test) 

stroopErr_control_mild_t.test_tidy <- stroopErr_control_mild_t.test_tidy %>% 
  mutate(task = "stroop_errors", groups = "control_mild")
```

###Retrieval-induced forgetting
```{r t-test control-mild retrieval-induced forgetting}
RIFdiff_control_mild_t.test <- t.test(controls$RIF_Diff, mild_tin$RIF_Diff, alternative = "greater",var.equal = F)#controls greater than mild
```

```{r tidy control-mild retrieval-induced forgetting t-test to extract coefficients}
RIFdiff_control_mild_t.test_tidy <- tidy(RIFdiff_control_mild_t.test) 

RIFdiff_control_mild_t.test_tidy <- RIFdiff_control_mild_t.test_tidy %>% 
  mutate(task = "RIF_diff", groups = "control_mild")
```

###Rule-switching
####Switch cost
```{r control-mild t-test switch cost}
switchcost_control_mild_t.test <- t.test(controls$switch_cost, mild_tin$switch_cost, alternative = "less",var.equal = F)#controls less than mild
```

```{r tidy control-mild switch cost t-test to extract coefficients}
switchcost_control_mild_t.test_tidy <- tidy(switchcost_control_mild_t.test) 

switchcost_control_mild_t.test_tidy <- switchcost_control_mild_t.test_tidy %>% 
  mutate(task = "switch_cost", groups = "control_mild")
```

####Errors
```{r control-mild t-test rule-switching errors}
switchErr_control_mild_t.test <- t.test(controls$rule_errors, mild_tin$rule_errors, alternative = "less",var.equal = F)#controls less than mild
```

```{r tidy control-mild rule-switching errors t-test to extract coefficients}
switchErr_control_mild_t.test_tidy <- tidy(switchErr_control_mild_t.test) 

switchErr_control_mild_t.test_tidy <- switchErr_control_mild_t.test_tidy %>% 
  mutate(task = "switch_errors", groups = "control_mild")
```

###Dual task
```{r t-test control-mild dual task}
dualtask_control_mild_t.test <- t.test(controls$dual_task_total, mild_tin$dual_task_total, alternative = "greater",var.equal = F)#controls greater than mild
```

```{r tidy control-mild dual task t-test to extract coefficients}
dualtask_control_mild_t.test_tidy <- tidy(dualtask_control_mild_t.test) 

dualtask_control_mild_t.test_tidy <- dualtask_control_mild_t.test_tidy %>% 
  mutate(task = "dual_task", groups = "control_mild")
```

###Matrix reasoning

```{r control-mild t-test matrix reasoning}
matrix_control_mild_t.test <- t.test(controls$matrixReason, mild_tin$matrixReason, alternative = "greater",var.equal = F)#controls greater than mild
```

```{r tidy control-mild matrix reasoning t-test to extract coefficients}
matrix_control_mild_t.test_tidy <- tidy(matrix_control_mild_t.test) 

matrix_control_mild_t.test_tidy <- matrix_control_mild_t.test_tidy %>% 
  mutate(task = "matrix_reasoning", groups = "control_mild")
```

##Controls and Modsev
###Number-letter sequencing
```{r t-test control-modsev letter-number sequencing}
nls_control_modsev_t.test <- t.test(controls$nls_correct, modsev_tin$nls_correct, alternative = "greater",var.equal = F)#controls greater than modsev

```

```{r tidy control-modsev letter-number sequencing t-test to extract coefficients}
nls_control_modsev_t.test_tidy <- tidy(nls_control_modsev_t.test)

nls_control_modsev_t.test_tidy <- nls_control_modsev_t.test_tidy %>% 
  mutate(task = "number_letter_sequencing", groups = "control_modsev")
```

###Keep-track
```{r t-test control-modsev keep-track}
keeptrack_control_modsev_t.test <- t.test(controls$keepTrack, modsev_tin$keepTrack, alternative = "greater",var.equal = F)#controls greater than modsev
```

```{r tidy control-modsev keep-track t-test to extract coefficients}
keeptrack_control_modsev_t.test_tidy <- tidy(keeptrack_control_modsev_t.test)

keeptrack_control_modsev_t.test_tidy <- keeptrack_control_modsev_t.test_tidy %>% 
  mutate(task = "keeptrack", groups = "control_modsev")
```

###Stroop
####Response time (incongruent)
```{r t-test control-modsev stroop}
stroopRT_control_modsev_t.test <- t.test(controls$stroop_incongruent, modsev_tin$stroop_incongruent, alternative = "less",var.equal = F)#controls less than modsev
```

```{r tidy control-modsev stroop t-test to extract coefficients}
stroopRT_control_modsev_t.test_tidy <- tidy(stroopRT_control_modsev_t.test)

stroopRT_control_modsev_t.test_tidy <- stroopRT_control_modsev_t.test_tidy %>% 
  mutate(task = "stroop_rt", groups = "control_modsev")
```

####Errors
```{r t-test control-modsev stroop errors}
stroopErr_control_modsev_t.test <- t.test(controls$stroop_errors, modsev_tin$stroop_errors, alternative = "less",var.equal = F)#controls less than modsev
```

```{r tidy control-modsev stroop errors t-test to extract coefficients}
stroopErr_control_modsev_t.test_tidy <- tidy(stroopErr_control_modsev_t.test) 

stroopErr_control_modsev_t.test_tidy <- stroopErr_control_modsev_t.test_tidy %>% 
  mutate(task = "stroop_errors", groups = "control_modsev")
```

###Retrieval-induced forgetting
```{r t-test control-modsev retrieval-induced forgetting}
RIFdiff_control_modsev_t.test <- t.test(controls$RIF_Diff, modsev_tin$RIF_Diff, alternative = "greater",var.equal = F)#controls greater than modsev
```

```{r tidy control-modsev retrieval-induced forgetting t-test to extract coefficients}
RIFdiff_control_modsev_t.test_tidy <- tidy(RIFdiff_control_modsev_t.test) 

RIFdiff_control_modsev_t.test_tidy <- RIFdiff_control_modsev_t.test_tidy %>% 
  mutate(task = "RIF_diff", groups = "control_modsev")
```

###Rule-switching
####Switch cost
```{r control-modsev t-test switch cost}
switchcost_control_modsev_t.test <- t.test(controls$switch_cost, modsev_tin$switch_cost, alternative = "less",var.equal = F)#controls less than modsev
```

```{r tidy control-modsev switch cost t-test to extract coefficients}
switchcost_control_modsev_t.test_tidy <- tidy(switchcost_control_modsev_t.test) 

switchcost_control_modsev_t.test_tidy <- switchcost_control_modsev_t.test_tidy %>% 
  mutate(task = "switch_cost", groups = "control_modsev")
```

####Errors
```{r control-modsev t-test rule-switching errors}
switchErr_control_modsev_t.test <- t.test(controls$rule_errors, modsev_tin$rule_errors, alternative = "less",var.equal = F)#controls less than modsev
```

```{r tidy control-modsev rule-switching errors t-test to extract coefficients}
switchErr_control_modsev_t.test_tidy <- tidy(switchErr_control_modsev_t.test) 

switchErr_control_modsev_t.test_tidy <- switchErr_control_modsev_t.test_tidy %>% 
  mutate(task = "switch_errors", groups = "control_modsev")
```

###Dual task
```{r t-test control-modsev dual task}
dualtask_control_modsev_t.test <- t.test(controls$dual_task_total, modsev_tin$dual_task_total, alternative = "greater",var.equal = F)#controls greater than modsev
```

```{r tidy control-modsev dual task t-test to extract coefficients}
dualtask_control_modsev_t.test_tidy <- tidy(dualtask_control_modsev_t.test) 

dualtask_control_modsev_t.test_tidy <- dualtask_control_modsev_t.test_tidy %>% 
  mutate(task = "dual_task", groups = "control_modsev")
```

###Matrix reasoning
```{r control-modsev t-test matrix reasoning}
matrix_control_modsev_t.test <- t.test(controls$matrixReason, modsev_tin$matrixReason, alternative = "greater",var.equal = F)#controls greater than modsev
```

```{r tidy control-modsev matrix reasoning t-test to extract coefficients}
matrix_control_modsev_t.test_tidy <- tidy(matrix_control_modsev_t.test) 

matrix_control_modsev_t.test_tidy <- matrix_control_modsev_t.test_tidy %>% 
  mutate(task = "matrix_reasoning", groups = "control_modsev")
```

##Mild and Modsev
###Number-letter sequencing
```{r t-test mild-modsev letter-number sequencing}
nls_mild_modsev_t.test <- t.test(mild_tin$nls_correct, modsev_tin$nls_correct, alternative = "greater",var.equal = F)#mild greater than modsev

```

```{r tidy mild-modsev letter-number sequencing t-test to extract coefficients}
nls_mild_modsev_t.test_tidy <- tidy(nls_mild_modsev_t.test)

nls_mild_modsev_t.test_tidy <- nls_mild_modsev_t.test_tidy %>% 
  mutate(task = "number_letter_sequencing", groups = "mild_modsev")
```

###Keep-track
```{r t-test mild-modsev keep-track}
keeptrack_mild_modsev_t.test <- t.test(mild_tin$keepTrack, modsev_tin$keepTrack, alternative = "greater",var.equal = F)#milds greater than modsev
```

```{r tidy mild-modsev keep-track t-test to extract coefficients}
keeptrack_mild_modsev_t.test_tidy <- tidy(keeptrack_mild_modsev_t.test)

keeptrack_mild_modsev_t.test_tidy <- keeptrack_mild_modsev_t.test_tidy %>% 
  mutate(task = "keeptrack", groups = "mild_modsev")
```

###Stroop
####Response time (incongruent)
```{r t-test mild-modsev stroop}
stroopRT_mild_modsev_t.test <- t.test(mild_tin$stroop_incongruent, modsev_tin$stroop_incongruent, alternative = "less",var.equal = F)#milds less than modsev
```

```{r tidy mild-modsev stroop t-test to extract coefficients}
stroopRT_mild_modsev_t.test_tidy <- tidy(stroopRT_mild_modsev_t.test)

stroopRT_mild_modsev_t.test_tidy <- stroopRT_mild_modsev_t.test_tidy %>% 
  mutate(task = "stroop_rt", groups = "mild_modsev")
```

####Errors
```{r t-test mild-modsev stroop errors}
stroopErr_mild_modsev_t.test <- t.test(mild_tin$stroop_errors, modsev_tin$stroop_errors, alternative = "less",var.equal = F)#milds less than modsev
```

```{r tidy mild-modsev stroop errors t-test to extract coefficients}
stroopErr_mild_modsev_t.test_tidy <- tidy(stroopErr_mild_modsev_t.test) 

stroopErr_mild_modsev_t.test_tidy <- stroopErr_mild_modsev_t.test_tidy %>% 
  mutate(task = "stroop_errors", groups = "mild_modsev")
```

###Retrieval-induced forgetting
```{r t-test mild-modsev retrieval-induced forgetting}
RIFdiff_mild_modsev_t.test <- t.test(mild_tin$RIF_Diff, modsev_tin$RIF_Diff, alternative = "greater",var.equal = F)#milds greater than modsev
```

```{r tidy mild-modsev retrieval-induced forgetting t-test to extract coefficients}
RIFdiff_mild_modsev_t.test_tidy <- tidy(RIFdiff_mild_modsev_t.test) 

RIFdiff_mild_modsev_t.test_tidy <- RIFdiff_mild_modsev_t.test_tidy %>% 
  mutate(task = "RIF_diff", groups = "mild_modsev")
```

###Rule-switching
####Switch cost
```{r mild-modsev t-test switch cost}
switchcost_mild_modsev_t.test <- t.test(mild_tin$switch_cost, modsev_tin$switch_cost, alternative = "less",var.equal = F)#milds less than modsev
```

```{r tidy mild-modsev switch cost t-test to extract coefficients}
switchcost_mild_modsev_t.test_tidy <- tidy(switchcost_mild_modsev_t.test) 

switchcost_mild_modsev_t.test_tidy <- switchcost_mild_modsev_t.test_tidy %>% 
  mutate(task = "switch_cost", groups = "mild_modsev")
```

####Errors
```{r mild-modsev t-test rule-switching errors}
switchErr_mild_modsev_t.test <- t.test(mild_tin$rule_errors, modsev_tin$rule_errors, alternative = "less",var.equal = F)#milds less than modsev
```

```{r tidy mild-modsev rule-switching errors t-test to extract coefficients}
switchErr_mild_modsev_t.test_tidy <- tidy(switchErr_mild_modsev_t.test) 

switchErr_mild_modsev_t.test_tidy <- switchErr_mild_modsev_t.test_tidy %>% 
  mutate(task = "switch_errors", groups = "mild_modsev")
```

###Dual task
```{r t-test mild-modsev dual task}
dualtask_mild_modsev_t.test <- t.test(mild_tin$dual_task_total, modsev_tin$dual_task_total, alternative = "greater",var.equal = F)#milds greater than modsev
```

```{r tidy mild-modsev dual task t-test to extract coefficients}
dualtask_mild_modsev_t.test_tidy <- tidy(dualtask_mild_modsev_t.test) 

dualtask_mild_modsev_t.test_tidy <- dualtask_mild_modsev_t.test_tidy %>% 
  mutate(task = "dual_task", groups = "mild_modsev")
```

###Matrix reasoning
```{r mild-modsev t-test matrix reasoning}
matrix_mild_modsev_t.test <- t.test(mild_tin$matrixReason, modsev_tin$matrixReason, alternative = "greater",var.equal = F)#milds greater than modsev
```

```{r tidy mild-modsev matrix reasoning t-test to extract coefficients}
matrix_mild_modsev_t.test_tidy <- tidy(matrix_mild_modsev_t.test) 

matrix_mild_modsev_t.test_tidy <- matrix_mild_modsev_t.test_tidy %>% 
  mutate(task = "matrix_reasoning", groups = "mild_modsev")
```

##Tables of t-test results
###Controls and Mild
```{r bind together tidy t.test results of control and milds}
t.test_table_control_mild <- bind_rows(nls_control_mild_t.test_tidy,
        keeptrack_control_mild_t.test_tidy,
        stroopRT_control_mild_t.test_tidy,
        stroopErr_control_mild_t.test_tidy,
        RIFdiff_control_mild_t.test_tidy,
        switchcost_control_mild_t.test_tidy,
        switchErr_control_mild_t.test_tidy,
        dualtask_control_mild_t.test_tidy,
        matrix_control_mild_t.test_tidy)


t.test_table_control_mild <- t.test_table_control_mild %>% 
  mutate(task = c("nls", "keeptrack", "stroopRT",
                  "stroopErr", "RIFdiff", "switch_cost",
                  "switch_error", "dual_task", "matrix_reason")) %>% 
  select(task, estimate, estimate1, estimate2, conf.low, conf.high, t.statistic = statistic, deg.of.freedom = parameter, p.value, H1 = alternative) %>% 
  mutate_if(is.numeric, round, digits = 2) %>% 
  mutate(deg.of.freedom = round(deg.of.freedom)) %>% 
  arrange(p.value)

#The degrees of freedom ssociated with this variance estimate is approximated using the Welch–Satterthwaite equation:

```
t-test table control mild
`r knitr::kable(t.test_table_control_mild)`
###Controls and Modsev
```{r bind together tidy t.test results of control and modsev}
t.test_table_control_modsev <- bind_rows(nls_control_modsev_t.test_tidy,
        keeptrack_control_modsev_t.test_tidy,
        stroopRT_control_modsev_t.test_tidy,
        stroopErr_control_modsev_t.test_tidy,
        RIFdiff_control_modsev_t.test_tidy,
        switchcost_control_modsev_t.test_tidy,
        switchErr_control_modsev_t.test_tidy,
        dualtask_control_modsev_t.test_tidy,
        matrix_control_modsev_t.test_tidy)

t.test_table_control_modsev <- t.test_table_control_modsev %>% 
  mutate(task = c("nls", "keeptrack", "stroopRT",
                  "stroopErr", "RIFdiff", "switch_cost",
                  "switch_error", "dual_task", "matrix_reason")) %>% 
  select(task, estimate, estimate1, estimate2, conf.low, conf.high, t.statistic = statistic, deg.of.freedom = parameter, p.value, H1 = alternative) %>% 
  mutate_if(is.numeric, round, digits = 2) %>% 
  mutate(deg.of.freedom = round(deg.of.freedom)) %>% 
  arrange(p.value)
```    
t-test table control modsev
`r knitr::kable(t.test_table_control_modsev)`
###Mild and Modsev
```{r bind together tidy t.test results of mild and modsev}
t.test_table_mild_modsev <- bind_rows(nls_mild_modsev_t.test_tidy,
        keeptrack_mild_modsev_t.test_tidy,
        stroopRT_mild_modsev_t.test_tidy,
        stroopErr_mild_modsev_t.test_tidy,
        RIFdiff_mild_modsev_t.test_tidy,
        switchcost_mild_modsev_t.test_tidy,
        switchErr_mild_modsev_t.test_tidy,
        dualtask_mild_modsev_t.test_tidy,
        matrix_mild_modsev_t.test_tidy)

t.test_table_mild_modsev <- t.test_table_mild_modsev %>% 
  mutate(task = c("nls", "keeptrack", "stroopRT",
                  "stroopErr", "RIFdiff", "switch_cost",
                  "switch_error", "dual_task", "matrix_reason")) %>% 
  select(task, estimate, estimate1, estimate2, conf.low, conf.high, t.statistic = statistic, deg.of.freedom = parameter, p.value, H1 = alternative) %>% 
  mutate_if(is.numeric, round, digits = 2) %>% 
  mutate(deg.of.freedom = round(deg.of.freedom)) %>% 
  arrange(p.value)
``` 
t-test table mild modsev
`r knitr::kable(t.test_table_mild_modsev)`
#Cohen's d
```{r calculate cohens d for all tasks}
#effect size for RIF effect
rif_cd_control_modsev <- cohens_d(controls$RIF_Diff, modsev_tin$RIF_Diff)#controls vs modsev
rif_cd_control_mild <- cohens_d(controls$RIF_Diff, mild_tin$RIF_Diff)#controls vs mild
rif_cd_mild_modsev <- cohens_d(mild_tin$RIF_Diff, modsev_tin$RIF_Diff) #mild vs modsev

#effect size for NLS scores
nls_cd_control_modsev <- cohens_d(controls$nls_correct, modsev_tin$nls_correct)#controls vs modsev
nls_cd_control_mild <- cohens_d(controls$nls_correct, mild_tin$nls_correct)#controls vs mild
nls_cd_mild_modsev <- cohens_d(mild_tin$nls_correct, modsev_tin$nls_correct)#mild vs modsev

#effect size for keep track scores
keep_cd_control_modsev <- cohens_d(controls$keepTrack, modsev_tin$keepTrack)#controls vs modsev
keep_cd_control_mild <- cohens_d(controls$keepTrack, mild_tin$keepTrack)#controls vs mild
keep_cd_mild_modsev <- cohens_d(mild_tin$keepTrack, modsev_tin$keepTrack)#mild vs modsev

#effect size for matrix reasoning scores
matrix_cd_control_modsev <- cohens_d(controls$matrixReason, modsev_tin$matrixReason)#controls vs modsev
matrix_cd_control_mild <- cohens_d(controls$matrixReason, mild_tin$matrixReason)#controls vs mild
matrix_cd_mild_modsev <- cohens_d(mild_tin$matrixReason, modsev_tin$matrixReason)#mild vs modsev

#effect size for stroop response times
stroopRT_cd_control_modsev <- cohens_d(controls$stroop_incongruent, modsev_tin$stroop_incongruent)#controls vs modsev
stroopRT_cd_control_mild <- cohens_d(controls$stroop_incongruent, mild_tin$stroop_incongruent)#controls vs mild
stroopRT_cd_mild_modsev <- cohens_d(mild_tin$stroop_incongruent, modsev_tin$stroop_incongruent)#mild vs modsev

#effect size for stroop error counts
stroopERR_cd_control_modsev <- cohens_d(controls$stroop_errors, modsev_tin$stroop_errors)#controls vs modsev
stroopERR_cd_control_mild <- cohens_d(controls$stroop_errors, mild_tin$stroop_errors)#controls vs mild
stroopERR_cd_mild_modsev <- cohens_d(mild_tin$stroop_errors, modsev_tin$stroop_errors)#mild vs modsev

#effect size for switch cost
switchCostRT_cd_control_modsev <- cohens_d(controls$switch_cost, modsev_tin$switch_cost)#controls vs modsev
switchCostRT_cd_control_mild <- cohens_d(controls$switch_cost, mild_tin$switch_cost)#controls vs mild
switchCostRT_cd_mild_modsev <- cohens_d(mild_tin$switch_cost, modsev_tin$switch_cost)#mild vs modsev

#effect size for rule switch errors
switchErr_cd_control_modsev <- cohens_d(controls$rule_errors, modsev_tin$rule_errors)#controls vs modsev
switchErr_cd_control_mild <- cohens_d(controls$rule_errors, mild_tin$rule_errors)#controls vs mild
switchErr_cd_mild_modsev <- cohens_d(mild_tin$rule_errors, modsev_tin$rule_errors)#mild vs modsev

#effect size for dual task numbers score
dual_cd_control_modsev <- cohens_d(controls$dual_task_total, modsev_tin$dual_task_total)#controls vs modsev
dual_cd_control_mild <- cohens_d(controls$dual_task_total, mild_tin$dual_task_total)#controls vs mild
dual_cd_mild_modsev <- cohens_d(mild_tin$dual_task_total, modsev_tin$dual_task_total)#mild vs modsev
```

```{r cohens d confidence interval control-mild}
#create group count variable
groupCount <- efit %>% 
  group_by(THI_cat) %>% 
  summarise(group_count = n())

#cohens_d confidence intervals for controls vs mild
rif_cd_control_mild_CI <- d.ci(rif_cd_control_mild, n1=groupCount$group_count[1], n2=groupCount$group_count[2])#confidence interval for RIF
nls_cd_control_mild_CI <- d.ci(nls_cd_control_mild, n1=groupCount$group_count[1], n2=groupCount$group_count[2])#confidence interval for nls
keep_cd_control_mild_CI <- d.ci(keep_cd_control_mild, n1=groupCount$group_count[1], n2=groupCount$group_count[2])#confidence interval for keep track
matrix_cd_control_mild_CI <- d.ci(matrix_cd_control_mild, n1=groupCount$group_count[1], n2=groupCount$group_count[2])#confidence interval for matrix reasoning
stroopRT_cd_control_mild_CI <- d.ci(stroopRT_cd_control_mild , n1=groupCount$group_count[1], n2=groupCount$group_count[2])#confidence interval for Stroop RT
stroopERR_cd_control_mild_CI <- d.ci(stroopERR_cd_control_mild , n1=groupCount$group_count[1], n2=groupCount$group_count[2])#confidence interval for Stroop errors
switchCostRT_cd_control_mild_CI <- d.ci(switchCostRT_cd_control_mild , n1=groupCount$group_count[1], n2=groupCount$group_count[2])#confidence interval for switch cost
switchErr_cd_control_mild_CI <- d.ci(switchErr_cd_control_mild , n1=groupCount$group_count[1], n2=groupCount$group_count[2])#confidence interval for switch errors
dual_cd_control_mildCI <- d.ci(dual_cd_control_mild , n1=groupCount$group_count[1], n2=groupCount$group_count[2])#confidence interval for dual task
```

```{r cohens d confidence intervals control-modsev}
#cohens_d confidence intervals for controls vs modsev
rif_cd_control_modsev_CI <- d.ci(rif_cd_control_modsev, n1=groupCount$group_count[1], n2=groupCount$group_count[3])#confidence interval for RIF

nls_cd_control_modsev_CI <- d.ci(nls_cd_control_modsev, n1=groupCount$group_count[1], n2=groupCount$group_count[3])#confidence interval for nls

keep_cd_control_modsev_CI <- d.ci(keep_cd_control_modsev, n1=groupCount$group_count[1], n2=groupCount$group_count[3])#confidence interval for keep track

matrix_cd_control_modsev_CI <- d.ci(matrix_cd_control_modsev, n1=groupCount$group_count[1], n2=groupCount$group_count[3])#confidence interval for matrix reasoning

stroopRT_cd_control_modsev_CI <- d.ci(stroopRT_cd_control_modsev , n1=groupCount$group_count[1], n2=groupCount$group_count[3])#confidence interval for Stroop RT
stroopERR_cd_control_modsev_CI <- d.ci(stroopERR_cd_control_modsev , n1=groupCount$group_count[1], n2=groupCount$group_count[3])#confidence interval for Stroop errors
switchCostRT_cd_control_modsev_CI <- d.ci(switchCostRT_cd_control_modsev , n1=groupCount$group_count[1], n2=groupCount$group_count[3])#confidence interval for switch cost
switchErr_cd_control_modsev_CI <- d.ci(switchErr_cd_control_modsev , n1=groupCount$group_count[1], n2=groupCount$group_count[3])#confidence interval for switch errors
dual_cd_control_modsevCI <- d.ci(dual_cd_control_modsev , n1=groupCount$group_count[1], n2=groupCount$group_count[3])#confidence interval for dual task
```

```{r cohens d confidence intervals mild-modsev}
#cohens_d confidence intervals for controls vs modsev
rif_cd_mild_modsev_CI <- d.ci(rif_cd_mild_modsev, n1=groupCount$group_count[2], n2=groupCount$group_count[3])#confidence interval for RIF
nls_cd_mild_modsev_CI <- d.ci(nls_cd_mild_modsev, n1=groupCount$group_count[2], n2=groupCount$group_count[3])#confidence interval for nls
keep_cd_mild_modsev_CI <- d.ci(keep_cd_mild_modsev, n1=groupCount$group_count[2], n2=groupCount$group_count[3])#confidence interval for keep track
matrix_cd_mild_modsev_CI <- d.ci(matrix_cd_mild_modsev, n1=groupCount$group_count[2], n2=groupCount$group_count[3])#confidence interval for matrix reasoning
stroopRT_cd_mild_modsev_CI <- d.ci(stroopRT_cd_mild_modsev , n1=groupCount$group_count[2], n2=groupCount$group_count[3])#confidence interval for Stroop RT
stroopERR_cd_mild_modsev_CI <- d.ci(stroopERR_cd_mild_modsev , n1=groupCount$group_count[2], n2=groupCount$group_count[3])#confidence interval for Stroop errors
switchCostRT_cd_mild_modsev_CI <- d.ci(switchCostRT_cd_mild_modsev , n1=groupCount$group_count[2], n2=groupCount$group_count[3])#confidence interval for switch cost
switchErr_cd_mild_modsev_CI <- d.ci(switchErr_cd_mild_modsev , n1=groupCount$group_count[2], n2=groupCount$group_count[3])#confidence interval for switch errors
dual_cd_mild_modsevCI <- d.ci(dual_cd_mild_modsev , n1=groupCount$group_count[2], n2=groupCount$group_count[3])#confidence interval for dual task
```

```{r create table of cohens d and confidence intervals for control-mild}
#create dataframe of cohens_d scores for control vs mild
control_mild_cd <- data.frame(
  c("RIF", 
    "NLS", 
    "keep track", 
    "matrix",
    "stroop RT", 
    "stroop errors", 
    "switch-cost", 
    "switch errors", 
    "dual task"),
  c(rif_cd_control_mild, 
    nls_cd_control_mild, 
    keep_cd_control_mild, 
    matrix_cd_control_mild, 
    stroopRT_cd_control_mild, 
    stroopERR_cd_control_mild, 
    switchCostRT_cd_control_mild,
    switchErr_cd_control_mild, 
    dual_cd_control_mild),
  c(rif_cd_control_mild_CI[1], 
    nls_cd_control_mild_CI[1], 
    keep_cd_control_mild_CI[1], 
    matrix_cd_control_mild_CI[1], 
    stroopRT_cd_control_mild_CI[1], 
    stroopERR_cd_control_mild_CI[1], 
    switchCostRT_cd_control_mild_CI[1],
    switchErr_cd_control_mild_CI[1], 
    dual_cd_control_mildCI[1]),
  c(rif_cd_control_mild_CI[3], 
    nls_cd_control_mild_CI[3], 
    keep_cd_control_mild_CI[3], 
    matrix_cd_control_mild_CI[3], 
    stroopRT_cd_control_mild_CI[3], 
    stroopERR_cd_control_mild_CI[3], 
    switchCostRT_cd_control_mild_CI[3],
    switchErr_cd_control_mild_CI[3], 
    dual_cd_control_mildCI[3]),
  c(rep("control vs tinnitus", 9))
)
colnames(control_mild_cd) <- c("task", "cohens_d", "CI_lower","CI_upper", "group")
```

```{r create table of cohens d and confidence intervals for controls-modsev}
#create dataframe of cohens_d scores for control vs modsev
control_modsev_cd <- data.frame(
  c("RIF", 
    "NLS", 
    "keep track", 
    "matrix",
    "stroop RT", 
    "stroop errors", 
    "switch-cost", 
    "switch errors", 
    "dual task"),
  c(rif_cd_control_modsev, 
    nls_cd_control_modsev, 
    keep_cd_control_modsev, 
    matrix_cd_control_modsev, 
    stroopRT_cd_control_modsev, 
    stroopERR_cd_control_modsev, 
    switchCostRT_cd_control_modsev,
    switchErr_cd_control_modsev, 
    dual_cd_control_modsev),
  c(rif_cd_control_modsev_CI[1], 
    nls_cd_control_modsev_CI[1], 
    keep_cd_control_modsev_CI[1], 
    matrix_cd_control_modsev_CI[1], 
    stroopRT_cd_control_modsev_CI[1], 
    stroopERR_cd_control_modsev_CI[1], 
    switchCostRT_cd_control_modsev_CI[1],
    switchErr_cd_control_modsev_CI[1], 
    dual_cd_control_modsevCI[1]),
  c(rif_cd_control_modsev_CI[3], 
    nls_cd_control_modsev_CI[3], 
    keep_cd_control_modsev_CI[3], 
    matrix_cd_control_modsev_CI[3], 
    stroopRT_cd_control_modsev_CI[3], 
    stroopERR_cd_control_modsev_CI[3],
    switchCostRT_cd_control_modsev_CI[3],
    switchErr_cd_control_modsev_CI[3], 
    dual_cd_control_modsevCI[3]),
  c(rep("control vs bothersome tinnitus", 9))
  )
colnames(control_modsev_cd) <- c("task", "cohens_d", "CI_lower","CI_upper", "group")
```

```{r create table of cohens d and confidence intervals for mild-modsev}
#create dataframe of cohens_d scores for mild vs modsev
mild_modsev_cd <- data.frame(
  c("RIF", 
    "NLS", 
    "keep track", 
    "matrix",
    "stroop RT", 
    "stroop errors", 
    "switch-cost", 
    "switch errors", 
    "dual task"),
  c(rif_cd_mild_modsev, 
    nls_cd_mild_modsev, 
    keep_cd_mild_modsev, 
    matrix_cd_mild_modsev, 
    stroopRT_cd_mild_modsev, 
    stroopERR_cd_mild_modsev, 
    switchCostRT_cd_mild_modsev,
    switchErr_cd_mild_modsev, 
    dual_cd_mild_modsev),
  c(rif_cd_mild_modsev_CI[1], 
    nls_cd_mild_modsev_CI[1], 
    keep_cd_mild_modsev_CI[1], 
    matrix_cd_mild_modsev_CI[1], 
    stroopRT_cd_mild_modsev_CI[1], 
    stroopERR_cd_mild_modsev_CI[1], 
    switchCostRT_cd_mild_modsev_CI[1],
    switchErr_cd_mild_modsev_CI[1], 
    dual_cd_mild_modsevCI[1]),
  c(rif_cd_mild_modsev_CI[3], 
    nls_cd_mild_modsev_CI[3], 
    keep_cd_mild_modsev_CI[3], 
    matrix_cd_mild_modsev_CI[3], 
    stroopRT_cd_mild_modsev_CI[3], 
    stroopERR_cd_mild_modsev_CI[3], 
    switchCostRT_cd_mild_modsev_CI[3],
    switchErr_cd_mild_modsev_CI[3], 
    dual_cd_mild_modsevCI[3]),
  c(rep("tinnitus vs bothersome tinnitus", 9))
  )
colnames(mild_modsev_cd) <- c("task", "cohens_d", "CI_lower","CI_upper", "group")
```

```{r join all cohens d and confidence interval tables}
#join all cohens d and ci tables together
all_groups_cohens_ci <- bind_rows(control_mild_cd, control_modsev_cd, mild_modsev_cd)

all_groups_cohens_ci$group <- as.factor(all_groups_cohens_ci$group)
```
#
all groups cohen's d
`r knitr::kable(all_groups_cohens_ci, digits = 2)`

```{r filtered table for control-mild and control-moderate cohens d plot}
control_mild_control_modsev_cohensd_ci <- all_groups_cohens_ci %>% 
  filter(group != "tinnitus vs bothersome tinnitus")#filter all group cohens d table for control-mild and control-modsev

control_mild_control_modsev_cohensd_ci <- control_mild_control_modsev_cohensd_ci %>% arrange(task,cohens_d)#arrange for easier transform

control_mild_control_modsev_cohensd_ci[11:18,2:4] <- control_mild_control_modsev_cohensd_ci[11:18,2:4]*-1#transofrm direction of response time and error tasks for easier interpretation - now all effect size represents performance relative to reference group. So in this instance, the control is the reference and a negative effect size is poorer performance on that task

#round confidence intervals and lower/upper bounds to 1 dececimal place
control_mild_control_modsev_cohensd_ci$cohens_d <- round(control_mild_control_modsev_cohensd_ci$cohens_d,1)
control_mild_control_modsev_cohensd_ci$CI_lower <- round(control_mild_control_modsev_cohensd_ci$CI_lower,2)
control_mild_control_modsev_cohensd_ci$CI_upper <- round(control_mild_control_modsev_cohensd_ci$CI_upper,2)

```

```{r cohens d plot of control-mild and control-modsev, eval = F}
#plot of cohens_d for control vs modsev and control vs mild for each task
SDMplot_controlVS <- control_mild_control_modsev_cohensd_ci %>% 
ggplot(aes(x = fct_rev(task), y = cohens_d, colour = group)) +
  geom_point(shape = 15, size = 3, position = position_dodge(width=0.5)) +
  geom_errorbar(alpha = 0.5, aes(ymin=CI_lower, ymax=CI_upper), position=position_dodge(width=0.5)) +
  geom_hline(yintercept = 0, linetype = "longdash") +
    coord_flip() +
  theme_cowplot() +
  scale_y_continuous(breaks = c(-1.2,-1,-.8,-.6,-.4,-.2,0,.2,.4,.6,.8,1)) +
  scale_color_viridis(discrete = TRUE, option = "D") +
  theme(legend.title = element_blank(),
        legend.text=element_text(size=8),
        axis.text.x = element_text(size = 8),
        axis.text.y = element_text(size = 8),
        plot.title = element_text(size = 10),
        legend.position="bottom",
        axis.title = element_text(size = 10),
        legend.justification = "centre")+
  xlab("Task") +
  ylab("Standardised Mean Difference") +
  labs(colour = "Comparison \nGroups") +
  ggtitle("Tinnitus and Bothersome Tinnitus Groups \nTask Performance Compared to \nControl Group")

ggsave("SDMplot_controlVS.tiff",plot = SDMplot_controlVS, units="in", width=5, height=4, dpi=400, compression = 'lzw')

```

```{r filtered table for control-mild and mild-moderate cohens d plot}
mild_control_mild_modsev_cohensd_ci <- all_groups_cohens_ci %>% 
  filter(group != "control vs bothersome tinnitus")#filter all group cohens d table for control-mild and mild-modsev

mild_control_mild_modsev_cohensd_ci[1:9,2:4] <- mild_control_mild_modsev_cohensd_ci[1:9,2:4]*-1 #reverse sign of all effect sizes for control vs tinnitus, so it now represents tinnitus vs control

mild_control_mild_modsev_cohensd_ci$group <- as.character(mild_control_mild_modsev_cohensd_ci$group)

mild_control_mild_modsev_cohensd_ci <- mild_control_mild_modsev_cohensd_ci %>% mutate(group = replace(group, group == "control vs tinnitus", "tinnitus vs control"))#label tinnitus as new reference group

mild_control_mild_modsev_cohensd_ci$group <- as.factor(mild_control_mild_modsev_cohensd_ci$group)

mild_control_mild_modsev_cohensd_ci <- mild_control_mild_modsev_cohensd_ci %>% arrange(task,cohens_d)#arrange for easier transform

mild_control_mild_modsev_cohensd_ci[11:18,2:4] <- mild_control_mild_modsev_cohensd_ci[11:18,2:4]*-1#transofrm direction of response time and error tasks for easier interpretation - now all effect size represents performance relative to reference group. So in this instance, the control is the reference and a negative effect size is poorer performance on that task

#round confidence intervals and lower/upper bounds to 1 dececimal place
mild_control_mild_modsev_cohensd_ci$cohens_d <- round(mild_control_mild_modsev_cohensd_ci$cohens_d,1)
mild_control_mild_modsev_cohensd_ci$CI_lower <- round(mild_control_mild_modsev_cohensd_ci$CI_lower,2)
mild_control_mild_modsev_cohensd_ci$CI_upper <- round(mild_control_mild_modsev_cohensd_ci$CI_upper,2)
```

```{r cohens d plot of mild-control and mild-modsev, eval= F}
#plot of cohens_d for mild vs modsev and mild vs control for each task
SDMplot_tinitusVS <- mild_control_mild_modsev_cohensd_ci %>% ggplot(aes(x = fct_rev(task), y = cohens_d, colour = group)) +
  geom_point(shape = 15, size = 3, position = position_dodge(width=0.5)) +
  geom_errorbar(alpha = 0.5, aes(ymin=CI_lower, ymax=CI_upper), position=position_dodge(width=0.5)) +
  geom_hline(yintercept = 0, linetype = "longdash") +
    coord_flip() +
  theme_cowplot() +
  scale_y_continuous(breaks = c(-1.2,-1,-.8,-.6,-.4,-.2,0,.2,.4,.6,.8,1)) +
  scale_color_viridis(discrete = TRUE, option = "D") +
  theme(legend.title = element_blank(),
        legend.text=element_text(size=8),
        axis.text.x = element_text(size = 8),
        axis.text.y = element_text(size = 8),
        plot.title = element_text(size = 10),
        legend.position="bottom",
        axis.title = element_text(size = 10),
        legend.justification = "centre")+
  xlab("Task") +
  ylab("Standardised Mean Difference") +
  labs(colour = "Comparison \nGroups") +
  ggtitle("Control and Bothersome Tinnitus Groups \nTask Performance Compared to \nTinnitus Group")

ggsave("SDMplot_tinnitusVS.tiff",plot = SDMplot_tinitusVS, units="in", width=5, height=4, dpi=400, compression = 'lzw')

```

```{r self report effect sizes}
CFQ_cd_control_mild <- cohens_d(controls$CFQ, mild_tin$CFQ)#controls vs mild

CFQ_cd_control_mild_CI <- d.ci(CFQ_cd_control_mild, n1=groupCount$group_count[1], n2=groupCount$group_count[2])#confidence interval for CFQ
round(CFQ_cd_control_mild_CI, digits = 3)

CFQ_cd_control_modsev <- cohens_d(controls$CFQ, modsev_tin$CFQ)#controls vs mild
CFQ_cd_control_modsev_CI <- d.ci(CFQ_cd_control_modsev, n1=groupCount$group_count[1], n2=groupCount$group_count[3])
round(CFQ_cd_control_modsev_CI, digits = 3)

RRS_cd_control_mild <- cohens_d(controls$RRS, mild_tin$RRS)#controls vs mild

RRS_cd_control_mild_CI <- d.ci(RRS_cd_control_mild, n1=groupCount$group_count[1], n2=groupCount$group_count[2])#confidence interval for RRS
round(RRS_cd_control_mild_CI, digits = 3)

RRS_cd_control_modsev <- cohens_d(controls$RRS, modsev_tin$RRS)#controls vs mild
RRS_cd_control_modsev_CI <- d.ci(RRS_cd_control_modsev, n1=groupCount$group_count[1], n2=groupCount$group_count[3])
round(RRS_cd_control_modsev_CI, digits = 3)
```


```{r convert cohens d to r for meta-analysis comparison}
tasks_d_to_r <- data.frame(task = control_mild_control_modsev_cohensd_ci$task , r = convert_d_to_r(control_mild_control_modsev_cohensd_ci$cohens_d), group = control_mild_control_modsev_cohensd_ci$group)

control_tinnitus_tasks_d_to_r <- tasks_d_to_r %>% 
  filter(group == "control vs tinnitus") %>% 
  mutate(meta_analysis_category = c(
    "switching",
    "updating",
    "fluid intelligence",
    "updating",
    "inhibition/glr",
    "inhibition",
    "inhibition",
    "switching",
    "switching"
  )) %>% 
  arrange(r)

control_bothersome_tinnitus_tasks_d_to_r <- tasks_d_to_r %>%
  filter(group == "control vs bothersome tinnitus") %>% 
  mutate(meta_analysis_category = c(
    "switching",
    "updating",
    "fluid intelligence",
    "updating",
    "inhibition/glr",
    "inhibition",
    "inhibition",
    "switching",
    "switching"
  )) %>% 
  arrange(r)
```

#
controls and tinnitus d to r
`r knitr::kable(control_tinnitus_tasks_d_to_r, digits = 2)`

#
controls and bothersome tinnitus d to r
`r knitr::kable(control_bothersome_tinnitus_tasks_d_to_r, digits = 2)`

#Bayesian t-tests
```{r bayesian t.test control-mild}
#Controls vs mild - drop modsev observations for bayesian t-test
bayes_control_mild <- efit %>% 
  filter(THI_cat != "bothersome tinnitus") %>% 
  droplevels()

#bayesian ttest for rule switch task - control vs mild
control_mild_switch_cost_BF <- BayesFactor::ttestBF(formula = switch_cost ~ THI_cat, data = bayes_control_mild)
BF_control_mild_switchCost <- describe_posterior(control_mild_switch_cost_BF)

#bayesian ttest for rule switch error - control vs mild
control_mild_switch_error_BF <- BayesFactor::ttestBF(formula = rule_errors ~ THI_cat, data = bayes_control_mild)
BF_control_mild_switchError <- describe_posterior(control_mild_switch_error_BF)

#bayesian ttest for stroop response time - control vs mild
control_mild_stroop_rt_BF <- BayesFactor::ttestBF(formula = stroop_incongruent ~ THI_cat, data = bayes_control_mild)
BF_control_mild_stroopRT <- describe_posterior(control_mild_stroop_rt_BF)

#bayesian ttest for stroop error count - control vs mild
control_mild_stroop_error_BF <- BayesFactor::ttestBF(formula = stroop_errors ~ THI_cat, data = bayes_control_mild)
BF_control_mild_stroopError <- describe_posterior(control_mild_stroop_error_BF)

#bayesian ttest for number letter sequencing - control vs mild
control_mild_nls_BF <- BayesFactor::ttestBF(formula = nls_correct ~ THI_cat, data = bayes_control_mild)
BF_control_mild_nls <- describe_posterior(control_mild_nls_BF)

#bayesian ttest for keep track task - control vs mild
control_mild_keep_BF <- BayesFactor::ttestBF(formula = keepTrack ~ THI_cat, data = bayes_control_mild)
BF_control_mild_keep <- describe_posterior(control_mild_keep_BF)

#bayesian ttest for RIF - control vs mild
control_mild_RIF_BF <- BayesFactor::ttestBF(formula = RIF_Diff ~ THI_cat, data = bayes_control_mild)
BF_control_mild_RIF <- describe_posterior(control_mild_RIF_BF)

#bayesian ttest for matrix reasoning - control vs mild
control_mild_matrix_BF <- BayesFactor::ttestBF(formula = matrixReason ~ THI_cat, data = bayes_control_mild)
BF_control_mild_matrix <- describe_posterior(control_mild_matrix_BF)

#bayesian ttest for dual task - control vs mild
control_mild_dual_BF <- BayesFactor::ttestBF(formula = dual_task_total ~ THI_cat, data = bayes_control_mild)
BF_control_mild_dual <- describe_posterior(control_mild_dual_BF)

#bayesian ttest for CFQ - control vs mild
control_mild_CFQ_BF <- BayesFactor::ttestBF(formula = CFQ ~ THI_cat, data = bayes_control_mild)
BF_control_mild_CFQ <- describe_posterior(control_mild_CFQ_BF)

#bayesian ttest for RRS - control vs mild
control_mild_RRS_BF <- BayesFactor::ttestBF(formula = RRS ~ THI_cat, data = bayes_control_mild)
BF_control_mild_RRS<- describe_posterior(control_mild_RRS_BF)

#bayesian ttest for CRIq_aged - control vs mild
control_mild_CRIq_aged_BF <- BayesFactor::ttestBF(formula = CRIq_aged ~ THI_cat, data = bayes_control_mild)
BF_control_mild_CRIq_aged <- describe_posterior(control_mild_CRIq_aged_BF)

#bayesian ttest for depression - control vs mild
control_mild_depression_BF <- BayesFactor::ttestBF(formula = CRIq_aged ~ THI_cat, data = bayes_control_mild)
BF_control_mild_depression <- describe_posterior(control_mild_depression_BF)

#bayesian ttest for anxiety - control vs mild
control_mild_anxiety_BF <- BayesFactor::ttestBF(formula = DASS_A ~ THI_cat, data = bayes_control_mild)
BF_control_mild_anxiety <- describe_posterior(control_mild_anxiety_BF)

#bayesian ttest for stress - control vs mild
control_mild_stress_BF <- BayesFactor::ttestBF(formula = DASS_S ~ THI_cat, data = bayes_control_mild)
BF_control_mild_stress <- describe_posterior(control_mild_stress_BF)
```

```{r bayesian t.test control-modsev}
#Controls vs modsev - drop mild observations for bayesian t-test
bayes_control_modsev <- efit %>% 
  filter(THI_cat != "tinnitus") %>% 
  droplevels()

#bayesian ttest for switch cost - control vs modsev
control_modsev_switch_cost_BF <- BayesFactor::ttestBF(formula = switch_cost ~ THI_cat, data = bayes_control_modsev)  
BF_control_modsev_switchCost <- describe_posterior(control_modsev_switch_cost_BF)

#bayesian ttest for rule switch error - control vs modsev
control_modsev_switch_error_BF <- BayesFactor::ttestBF(formula = rule_errors ~ THI_cat, data = bayes_control_modsev)
BF_control_modsev_switchError <- describe_posterior(control_modsev_switch_error_BF)

#bayesian ttest for stroop response time - control vs modsev
control_modsev_stroop_rt_BF <- BayesFactor::ttestBF(formula = stroop_incongruent ~ THI_cat, data = bayes_control_modsev)
BF_control_modsev_stroopRT <- describe_posterior(control_modsev_stroop_rt_BF)

#bayesian ttest for stroop error count - control vs modsev
control_modsev_stroop_error_BF <- BayesFactor::ttestBF(formula = stroop_errors ~ THI_cat, data = bayes_control_modsev)
BF_control_modsev_stroopError <- describe_posterior(control_modsev_stroop_error_BF)

#bayesian ttest for number letter sequencing - control vs modsev
control_modsev_nls_BF <- BayesFactor::ttestBF(formula = nls_correct ~ THI_cat, data = bayes_control_modsev)
BF_control_modsev_nls <- describe_posterior(control_modsev_nls_BF)

#bayesian ttest for keep track task - control vs modsev
control_modsev_keep_BF <- BayesFactor::ttestBF(formula = keepTrack ~ THI_cat, data = bayes_control_modsev)
BF_control_modsev_keep <- describe_posterior(control_modsev_keep_BF)

#bayesian ttest for RIF - control vs modsev
control_modsev_RIF_BF <- BayesFactor::ttestBF(formula = RIF_Diff ~ THI_cat, data = bayes_control_modsev)
BF_control_modsev_RIF <- describe_posterior(control_modsev_RIF_BF)

#bayesian ttest for matrix reasoning - control vs modsev
control_modsev_matrix_BF <- BayesFactor::ttestBF(formula = matrixReason ~ THI_cat, data = bayes_control_modsev)
BF_control_modsev_matrix <- describe_posterior(control_modsev_matrix_BF)

#bayesian ttest for dual task - control vs modsev
control_modsev_dual_BF <- BayesFactor::ttestBF(formula = dual_task_total ~ THI_cat, data = bayes_control_modsev)
BF_control_modsev_dual <- describe_posterior(control_modsev_dual_BF)

#bayesian ttest for CFQ - control vs modsev
control_modsev_CFQ_BF <- BayesFactor::ttestBF(formula = CFQ ~ THI_cat, data = bayes_control_modsev)
BF_control_modsev_CFQ <- describe_posterior(control_modsev_CFQ_BF)

#bayesian ttest for RRS - control vs modsev
control_modsev_RRS_BF <- BayesFactor::ttestBF(formula = RRS ~ THI_cat, data = bayes_control_modsev)
BF_control_modsev_RRS <- describe_posterior(control_modsev_RRS_BF)

#bayesian ttest for CRIq_aged - control vs modsev
control_modsev_CRIq_aged_BF <- BayesFactor::ttestBF(formula = CRIq_aged ~ THI_cat, data = bayes_control_modsev)
BF_control_modsev_CRIq_aged <- describe_posterior(control_modsev_CRIq_aged_BF)

#bayesian ttest for depression - control vs modsev
control_modsev_depression_BF <- BayesFactor::ttestBF(formula = CRIq_aged ~ THI_cat, data = bayes_control_modsev)
BF_control_modsev_depression <- describe_posterior(control_modsev_depression_BF)

#bayesian ttest for anxiety - control vs modsev
control_modsev_anxiety_BF <- BayesFactor::ttestBF(formula = DASS_A ~ THI_cat, data = bayes_control_modsev)
BF_control_modsev_anxiety <- describe_posterior(control_modsev_anxiety_BF)

#bayesian ttest for stress - control vs modsev
control_modsev_stress_BF <- BayesFactor::ttestBF(formula = DASS_S ~ THI_cat, data = bayes_control_modsev)
BF_control_modsev_stress <- describe_posterior(control_modsev_stress_BF)
```

```{r bayesian t.test mild-modsev}
#mild vs modsev - drop modsev observations for bayesian t-test
bayes_mild_modsev <- efit %>% 
  filter(THI_cat != "control") %>% 
  droplevels()

#bayesian ttest for rule switch task - mild vs modsev
mild_modsev_switch_cost_BF <- BayesFactor::ttestBF(formula = switch_cost ~ THI_cat, data = bayes_mild_modsev)
BF_mild_modsev_switchCost <- describe_posterior(mild_modsev_switch_cost_BF)

#bayesian ttest for rule switch error - mild vs modsev
mild_modsev_switch_error_BF <- BayesFactor::ttestBF(formula = rule_errors ~ THI_cat, data = bayes_mild_modsev)
BF_mild_modsev_switchError <- describe_posterior(mild_modsev_switch_error_BF)

#bayesian ttest for stroop response time - mild vs modsev
mild_modsev_stroop_rt_BF <- BayesFactor::ttestBF(formula = stroop_incongruent ~ THI_cat, data = bayes_mild_modsev)
BF_mild_modsev_stroopRT <- describe_posterior(mild_modsev_stroop_rt_BF)

#bayesian ttest for stroop error count - mild vs modsev
mild_modsev_stroop_error_BF <- BayesFactor::ttestBF(formula = stroop_errors ~ THI_cat, data = bayes_mild_modsev)
BF_mild_modsev_stroopError <- describe_posterior(mild_modsev_stroop_error_BF)

#bayesian ttest for number letter sequencing - mild vs modsev
mild_modsev_nls_BF <- BayesFactor::ttestBF(formula = nls_correct ~ THI_cat, data = bayes_mild_modsev)
BF_mild_modsev_nls <- describe_posterior(mild_modsev_nls_BF)

#bayesian ttest for keep track task - mild vs modsev
mild_modsev_keep_BF <- BayesFactor::ttestBF(formula = keepTrack ~ THI_cat, data = bayes_mild_modsev)
BF_mild_modsev_keep <- describe_posterior(mild_modsev_keep_BF)

#bayesian ttest for RIF - mild vs modsev
mild_modsev_RIF_BF <- BayesFactor::ttestBF(formula = RIF_Diff ~ THI_cat, data = bayes_mild_modsev)
BF_mild_modsev_RIF <- describe_posterior(mild_modsev_RIF_BF)

#bayesian ttest for matrix reasoning - mild vs modsev
mild_modsev_matrix_BF <- BayesFactor::ttestBF(formula = matrixReason ~ THI_cat, data = bayes_mild_modsev)
BF_mild_modsev_matrix <- describe_posterior(mild_modsev_matrix_BF)

#bayesian ttest for dual task - mild vs modsev
mild_modsev_dual_BF <- BayesFactor::ttestBF(formula = dual_task_total ~ THI_cat, data = bayes_mild_modsev)
BF_mild_modsev_dual <- describe_posterior(mild_modsev_dual_BF)

#bayesian ttest for CFQ - mild vs modsev
mild_modsev_CFQ_BF <- BayesFactor::ttestBF(formula = CFQ ~ THI_cat, data = bayes_mild_modsev)
BF_mild_modsev_CFQ <- describe_posterior(mild_modsev_CFQ_BF)

#bayesian ttest for RRS - mild vs modsev
mild_modsev_RRS_BF <- BayesFactor::ttestBF(formula = RRS ~ THI_cat, data = bayes_mild_modsev)
BF_mild_modsev_RRS<- describe_posterior(mild_modsev_RRS_BF)

#bayesian ttest for CRIq_aged - mild vs modsev
mild_modsev_CRIq_aged_BF <- BayesFactor::ttestBF(formula = CRIq_aged ~ THI_cat, data = bayes_mild_modsev)
BF_mild_modsev_CRIq_aged <- describe_posterior(mild_modsev_CRIq_aged_BF)

#bayesian ttest for depression - mild vs modsev
mild_modsev_depression_BF <- BayesFactor::ttestBF(formula = CRIq_aged ~ THI_cat, data = bayes_mild_modsev)
BF_mild_modsev_depression <- describe_posterior(mild_modsev_depression_BF)

#bayesian ttest for anxiety - mild vs modsev
mild_modsev_anxiety_BF <- BayesFactor::ttestBF(formula = DASS_A ~ THI_cat, data = bayes_mild_modsev)
BF_mild_modsev_anxiety <- describe_posterior(mild_modsev_anxiety_BF)

#bayesian ttest for stress - mild vs modsev
mild_modsev_stress_BF <- BayesFactor::ttestBF(formula = DASS_S ~ THI_cat, data = bayes_mild_modsev)
BF_mild_modsev_stress <- describe_posterior(mild_modsev_stress_BF)
```

```{r table of bayes factors for control-mild}
#create table of bayes factors for control vs mild
control_mild_BF <- data.frame(
  c("Retrieval-induced forgetting", 
    "Number letter sequencing", 
    "Keep track", 
    "Matrix reasoning",
    "Stroop-RT", 
    "Stroop-errors", 
    "Switch cost", 
    "Switch errors", 
    "Dual task",
    "CFQ",
    "RRS",
    "CRIq_aged",
    "Depression",
    "Anxiety",
    "Stress"),
  c(BF_control_mild_RIF$BF, 
    BF_control_mild_nls$BF, 
    BF_control_mild_keep$BF,
    BF_control_mild_matrix$BF,
    BF_control_mild_stroopRT$BF,
    BF_control_mild_stroopError$BF,
    BF_control_mild_switchCost$BF,
    BF_control_mild_switchError$BF,
    BF_control_mild_dual$BF,
    BF_control_mild_CFQ$BF,
    BF_control_mild_RRS$BF,
    BF_control_mild_CRIq_aged$BF,
    BF_control_mild_depression$BF,
    BF_control_mild_anxiety$BF,
    BF_control_mild_stress$BF)
)
colnames(control_mild_BF) <- c("name", "bayes_factor")
control_mild_BF$bayes_factor <- round(control_mild_BF$bayes_factor, 2)

control_mild_BF <- control_mild_BF %>% arrange(desc(bayes_factor))
```
table of control-mild BFs

`r knitr::kable(control_mild_BF)`
#
```{r table of bayes factors for control-modsev}
#bayes factor for control vs modsev
control_modsev_BF <- data.frame(
  c("Retrieval-induced forgetting", 
    "Number letter sequencing", 
    "Keep track", 
    "Matrix reasoning",
    "Stroop-RT", 
    "Stroop-errors", 
    "Switch cost", 
    "Switch errors", 
    "Dual task",
    "CFQ",
    "RRS",
    "CRIq_aged",
    "Depression",
    "Anxiety",
    "Stress"),
  c(BF_control_modsev_RIF$BF, 
    BF_control_modsev_nls$BF, 
    BF_control_modsev_keep$BF,
    BF_control_modsev_matrix$BF,
    BF_control_modsev_stroopRT$BF,
    BF_control_modsev_stroopError$BF,
    BF_control_modsev_switchCost$BF,
    BF_control_modsev_switchError$BF,
    BF_control_modsev_dual$BF,
    BF_control_modsev_CFQ$BF,
    BF_control_modsev_RRS$BF,
    BF_control_modsev_CRIq_aged$BF,
    BF_control_modsev_depression$BF,
    BF_control_modsev_anxiety$BF,
    BF_control_modsev_stress$BF)
)
colnames(control_modsev_BF) <- c("name", "bayes_factor")
control_modsev_BF$bayes_factor <- round(control_modsev_BF$bayes_factor, 2)

control_modsev_BF <- control_modsev_BF %>% arrange(desc(bayes_factor))
```
table of control-modsev BFs

`r knitr::kable(control_modsev_BF)`
#
```{r table of bayes factors for mild-modsev}
#create table of bayes factors for mild-modsev
mild_modsev_BF <- data.frame(
  c("Retrieval-induced forgetting", 
    "Number letter sequencing", 
    "Keep track", 
    "Matrix reasoning",
    "Stroop-RT", 
    "Stroop-errors", 
    "Switch cost", 
    "Switch errors", 
    "Dual task",
    "CFQ",
    "RRS",
    "CRIq_aged",
    "Depression",
    "Anxiety",
    "Stress"),
  c(BF_mild_modsev_RIF$BF, 
    BF_mild_modsev_nls$BF, 
    BF_mild_modsev_keep$BF,
    BF_mild_modsev_matrix$BF,
    BF_mild_modsev_stroopRT$BF,
    BF_mild_modsev_stroopError$BF,
    BF_mild_modsev_switchCost$BF,
    BF_mild_modsev_switchError$BF,
    BF_mild_modsev_dual$BF,
    BF_mild_modsev_CFQ$BF,
    BF_mild_modsev_RRS$BF,
    BF_mild_modsev_CRIq_aged$BF,
    BF_mild_modsev_depression$BF,
    BF_mild_modsev_anxiety$BF,
    BF_mild_modsev_stress$BF)
)
colnames(mild_modsev_BF) <- c("name", "bayes_factor")
mild_modsev_BF$bayes_factor <- round(mild_modsev_BF$bayes_factor, 2)

mild_modsev_BF <- mild_modsev_BF %>% arrange(desc(bayes_factor))
```
table of mild-modsev BFs

`r knitr::kable(mild_modsev_BF)`
#
#Linear regressions
##Data preparation
```{r linear regression data preparation}
efit$THI_cat <- as.integer(efit$THI_cat)

efit$THI_cat <- as.factor(efit$THI_cat)

efit <- efit %>% 
  mutate(nls_correct_scaled = scale(nls_correct),
         RIF_Diff_scaled = scale(RIF_Diff),
         keepTrack_scaled = scale(keepTrack),
         stroop_incongruent_scaled = scale(stroop_incongruent),
         stroop_errors_scaled = scale(stroop_errors),
         switch_cost_scaled = scale(switch_cost),
         rule_errors_scaled = scale(rule_errors),
         dual_task_total_scaled = scale(dual_task_total),
         matrixReason_scaled = scale(matrixReason),
         age_scaled = scale(age),
         hearThresh_scaled = scale(hearThresh),
         DASS_A_scaled = scale(DASS_A),
         DASS_D_scaled = scale(DASS_D),
         DASS_S_scaled = scale(DASS_S),
         CRIq_scaled = scale(CRIq),
         RRS_scaled = scale(RRS),
         pRIF_RpPlus_scaled = scale(pRIF_RpPlus),
         pRIF_RpMinus_scaled = scale(pRIF_RpMinus),
         pRIF_Np_scaled = scale(pRIF_Np)
         )
```
```{r linear regressions for CRIq}
CRIq_lm_tincats <- lm(formula = CRIq ~ THI_cat + age, data = efit)

summary(CRIq_lm_tincats)

CRIq_lm_tincats_scaled <- lm(formula = CRIq_scaled ~ THI_cat + age_scaled, data = efit)
```

##Number-letter sequencing
```{r nls THI groups lm}
nls_lm_tincats <- lm(formula = nls_correct ~ THI_cat + age + hearThresh + DASS_A + DASS_D + DASS_S, data = efit)

tidy_nls_lm_tincats <- tidy(nls_lm_tincats) %>% mutate(task = "nls_correct")

#create formula for calculating standardised partial regression coefficent to check against the scaled model: sp = b * (sd(IV)/sd(DV))
#stand_partial <- tidy_nls_lm_tincats$estimate[2]* sd(efit$age)/sd(efit$nls_correct) 

#standardised version of the model
nls_lm_tincats_scaled <- lm(formula = nls_correct_scaled ~ THI_cat + age_scaled + hearThresh_scaled + DASS_A_scaled + DASS_D_scaled + DASS_S_scaled, data = efit)

tidy_nls_lm_tincats_scaled <- tidy(nls_lm_tincats_scaled)

ranked_nls_lm_tincats_scaled <- tidy_nls_lm_tincats_scaled %>% 
  filter(term != "(Intercept)") %>% 
  mutate(partial_beta_rank = rank(estimate),
         task = "nls_correct")
```

##Keep track
```{r keeptrack THI groups lm}
keepTrack_lm_tincats <- lm(formula = keepTrack ~ THI_cat + age + hearThresh + DASS_A + DASS_D + DASS_S, data = efit)

tidy_keepTrack_lm_tincats <- tidy(keepTrack_lm_tincats) %>% mutate(task = "keep_track_correct")

keepTrack_lm_tincats_scaled <- lm(formula = keepTrack_scaled ~ THI_cat + age_scaled + hearThresh_scaled + DASS_A_scaled + DASS_D_scaled + DASS_S_scaled, data = efit)

tidy_keepTrack_lm_tincats_scaled <- tidy(keepTrack_lm_tincats_scaled)

ranked_keepTrack_lm_tincats_scaled <- tidy_keepTrack_lm_tincats_scaled %>% 
  filter(term != "(Intercept)") %>% 
  mutate(partial_beta_rank = rank(estimate),
         task = "keep_track_correct")
```
##Stroop
###RT
```{r stroop incong_rt THI groups lm}
stroopRT_lm_tincats <- lm(formula = stroop_incongruent ~ THI_cat + age + hearThresh + DASS_A + DASS_D + DASS_S, data = efit)

tidy_stroopRT_lm_tincats <- tidy(stroopRT_lm_tincats) %>% mutate(task = "stroop_incongruent_RT")

stroopRT_lm_tincats_scaled <- lm(formula = stroop_incongruent_scaled ~ THI_cat + age_scaled + hearThresh_scaled + DASS_A_scaled + DASS_D_scaled + DASS_S_scaled, data = efit)

tidy_stroopRT_lm_tincats_scaled <- tidy(stroopRT_lm_tincats_scaled)

ranked_stroopRT_lm_tincats_scaled <- tidy_stroopRT_lm_tincats_scaled %>% 
  filter(term != "(Intercept)") %>% 
  mutate(partial_beta_rank = rank(-estimate),
         task = "stroop_incongruent_rt")
```
###Errors
```{r stroop errors THI groups lm}
stroopErr_lm_tincats <- lm(formula = stroop_errors ~ THI_cat + age + hearThresh + DASS_A + DASS_D + DASS_S, data = efit)

tidy_stroopErr_lm_tincats <- tidy(stroopErr_lm_tincats) %>% mutate(task = "stroop_errors")

stroopErr_lm_tincats_scaled <- lm(formula = stroop_errors_scaled ~ THI_cat + age_scaled + hearThresh_scaled + DASS_A_scaled + DASS_D_scaled + DASS_S_scaled, data = efit)

tidy_stroopErr_lm_tincats_scaled <- tidy(stroopErr_lm_tincats_scaled)

ranked_stroopErr_lm_tincats_scaled <- tidy_stroopErr_lm_tincats_scaled %>% 
  filter(term != "(Intercept)") %>% 
  mutate(partial_beta_rank = rank(-estimate),
         task = "stroop_errors")
```
##RIF
```{r RIF difference THI groups lm}
RIF_diff_lm_tincats <- lm(formula = RIF_Diff ~ THI_cat + age + hearThresh + DASS_A + DASS_D + DASS_S, data = efit)

tidy_RIF_diff_lm_tincats <- tidy(RIF_diff_lm_tincats) %>% mutate(task = "RIF_difference")

RIF_diff_lm_tincats_scaled <- lm(formula = RIF_Diff_scaled ~ THI_cat + age_scaled + hearThresh_scaled + DASS_A_scaled + DASS_D_scaled + DASS_S_scaled, data = efit)

tidy_RIF_diff_lm_tincats_scaled <- tidy(RIF_diff_lm_tincats_scaled)

ranked_RIF_diff_lm_tincats_scaled  <- tidy_RIF_diff_lm_tincats_scaled %>% 
  filter(term != "(Intercept)") %>% 
  mutate(partial_beta_rank = rank(estimate),
         task = "RIF_difference")
```
##Rule-switch
###RT
```{r rule switchcost THI groups lm}
ruleSwitchCost_lm_tincats <- lm(formula = switch_cost ~ THI_cat + age + hearThresh + DASS_A + DASS_D + DASS_S, data = efit)

tidy_ruleSwitchCost_lm_tincats <- tidy(ruleSwitchCost_lm_tincats) %>% mutate(task = "rule_switch_cost")

ruleSwitchCost_lm_tincats_scaled <- lm(formula = switch_cost_scaled ~ THI_cat + age_scaled + hearThresh_scaled + DASS_A_scaled + DASS_D_scaled + DASS_S_scaled, data = efit)

tidy_ruleSwitchCost_lm_tincats_scaled <- tidy(ruleSwitchCost_lm_tincats_scaled)

ranked_ruleSwitchCost_lm_tincats_scaled  <- tidy_ruleSwitchCost_lm_tincats_scaled %>% 
  filter(term != "(Intercept)") %>% 
  mutate(partial_beta_rank = rank(-estimate),
         task = "rule_switch_cost")
```
###Errors
```{r rule errors THI groups lm}
ruleErr_lm_tincats <- lm(formula = rule_errors ~ THI_cat + age + hearThresh + DASS_A + DASS_D + DASS_S, data = efit)

tidy_ruleErr_lm_tincats <- tidy(ruleErr_lm_tincats) %>% mutate(task = "rule_switch_errors")

ruleErr_lm_tincats_scaled <- lm(formula = rule_errors_scaled ~ THI_cat + age_scaled + hearThresh_scaled + DASS_A_scaled + DASS_D_scaled + DASS_S_scaled, data = efit)

tidy_ruleErr_lm_tincats_scaled <- tidy(ruleErr_lm_tincats_scaled)

ranked_ruleErr_lm_tincats_scaled   <- tidy_ruleErr_lm_tincats_scaled %>% 
  filter(term != "(Intercept)") %>% 
  mutate(partial_beta_rank = rank(-estimate),
         task = "rule_switch_errors")
```
##Dual task
```{r dual task THI groups lm}
dualTask_lm_tincats <- lm(formula = dual_task_total ~ THI_cat + age + hearThresh + DASS_A + DASS_D + DASS_S, data = efit)

tidy_dualTask_lm_tincats <- tidy(dualTask_lm_tincats) %>% mutate(task = "dual_task_numbers_total")

dualTask_lm_tincats_scaled <- lm(formula = dual_task_total_scaled ~ THI_cat + age_scaled + hearThresh_scaled + DASS_A_scaled + DASS_D_scaled + DASS_S_scaled, data = efit)

tidy_dualTask_lm_tincats_scaled <- tidy(dualTask_lm_tincats_scaled)

ranked_dualTask_lm_tincats_scaled <- tidy_dualTask_lm_tincats_scaled %>% 
  filter(term != "(Intercept)") %>% 
  mutate(partial_beta_rank = rank(estimate),
         task = "dual_task_numbers_total")
```
##Matrix reasoning
```{r matrix reasoning THI groups lm}
matrixReason_lm_tincats <- lm(formula = matrixReason ~ THI_cat + age + hearThresh + DASS_A + DASS_D + DASS_S, data = efit)

tidy_matrixReason_lm_tincats <- tidy(matrixReason_lm_tincats) %>% mutate(task = "matrix_reasoning")

matrixReason_lm_tincats_scaled <- lm(formula = matrixReason_scaled ~ THI_cat + age_scaled + hearThresh_scaled + DASS_A_scaled + DASS_D_scaled + DASS_S_scaled, data = efit)

tidy_matrixReason_lm_tincats_scaled <- tidy(matrixReason_lm_tincats_scaled)

ranked_matrixReason_lm_tincats_scaled <- tidy_matrixReason_lm_tincats_scaled %>% 
  filter(term != "(Intercept)") %>% 
  mutate(partial_beta_rank = rank(estimate),
         task = "matrix_reasoning")
```

```{r bind tables for all non-scaled regressions}
all_lm_tincats <- rbind(
  tidy_nls_lm_tincats,
  tidy_dualTask_lm_tincats,
  tidy_keepTrack_lm_tincats,
  tidy_matrixReason_lm_tincats,
  tidy_RIF_diff_lm_tincats,
  tidy_ruleErr_lm_tincats,
  tidy_ruleSwitchCost_lm_tincats,
  tidy_stroopErr_lm_tincats,
  tidy_stroopRT_lm_tincats
) 

all_lm_tincats$term <- all_lm_tincats$term %>% 
  str_replace("THI_cat2", "tinnitus") %>% 
  str_replace("THI_cat3", "bothersome_tinnitus") 

all_lm_tincats <- all_lm_tincats%>% mutate_if(is.numeric, round, digits = 3)
```
table of all non-scaled linear models

`r knitr::kable(all_lm_tincats)`
#

```{r bind tables of all ranked lm results}
all_ranked_lm_tincats_scaled <- rbind(
  ranked_nls_lm_tincats_scaled,
  ranked_dualTask_lm_tincats_scaled,
  ranked_keepTrack_lm_tincats_scaled,
  ranked_matrixReason_lm_tincats_scaled,
  ranked_RIF_diff_lm_tincats_scaled,
  ranked_ruleErr_lm_tincats_scaled,
  ranked_ruleSwitchCost_lm_tincats_scaled,
  ranked_stroopErr_lm_tincats_scaled,
  ranked_stroopRT_lm_tincats_scaled
) 

all_ranked_lm_tincats_scaled$term <- all_ranked_lm_tincats_scaled$term %>% 
  str_replace("THI_cat2", "tinnitus") %>% 
  str_replace("THI_cat3", "bothersome_tinnitus")

all_ranked_lm_tincats_scaled <- all_ranked_lm_tincats_scaled %>% mutate_if(is.numeric, round, digits = 3)

stat_sig_linear_models <- all_ranked_lm_tincats_scaled %>% filter(p.value < 0.05)

```
table of all linera models

`r knitr::kable(all_ranked_lm_tincats_scaled)`
#
table of all statistically significant variables froma all linear models

`r knitr::kable(stat_sig_linear_models)`
#
```{r find ranks of bothersome tinnitus partial beta}
#create table of bothersome tinnitus group rank and estimates
bothersome_tinnitus_rank <- all_ranked_lm_tincats_scaled %>%
  filter(term == "bothersome_tinnitus") %>% 
  select(task, partial_beta_rank, estimate)

bothersome_tinnitus_rank$estimate <- round(bothersome_tinnitus_rank$estimate, digits = 2)

bothersome_tinnitus_rank <- bothersome_tinnitus_rank %>% 
  arrange(partial_beta_rank, estimate)
#create table of tinnitus group rank and estimates
tinnitus_rank <- all_ranked_lm_tincats_scaled %>%
  filter(term == "tinnitus") %>% 
  select(task, partial_beta_rank, estimate)

tinnitus_rank$estimate <- round(tinnitus_rank$estimate, digits = 2)

tinnitus_rank <- tinnitus_rank %>% 
  arrange(partial_beta_rank, estimate)

#some sort of table showng top 2 ranking variables by task
all_task_top_two_ranking <- all_ranked_lm_tincats_scaled %>% 
  #filter(task == "rule_switch_cost"|
   #      task == "rule_switch_errors"|
    #     task == "stroop_incongruent_rt"|
     #      task == "dual_task_words_diff") %>% 
  filter(partial_beta_rank == 1 |
           partial_beta_rank == 2) %>% 
  select(task,term, partial_beta_rank, estimate) %>% 
  arrange(task,partial_beta_rank, estimate)
```
table of bothersome tinnitus partial beta ranks
`r knitr::kable(bothersome_tinnitus_rank)`
#
table of tinnitus partial beta ranks
`r knitr::kable(tinnitus_rank)`
#
table all tasks, top two ranking variables

`r knitr::kable(all_task_top_two_ranking)`
#Retrieval-induced forgetting analysis
```{r means of all practise variables by THI group}
RIF_mean_table <- efit %>% 
  group_by(THI_cat) %>% 
  summarise(pRp_plus_mean = round(mean(pRIF_RpPlus)),
            pRp_minus_mean = round(mean(pRIF_RpMinus)),
            pNp_mean = round(mean(pRIF_Np)),
            pRIF_total_mean = round(mean(pRIF_total)),
            RIF_Diff_mean = round(mean(RIF_Diff)))

RIF_mean_table$THI_cat <- as.character(RIF_mean_table$THI_cat)

RIF_mean_table$THI_cat <- RIF_mean_table$THI_cat %>% 
  str_replace("1", "control") %>% 
  str_replace("2", "tinnitus") %>% 
  str_replace("3", "bothersome_tinnitus")
```
#
table RIF mean values
`r knitr::kable(RIF_mean_table)`

```{r linear models of rp_plus, rp_min, and Np}
rp_plus_lm <- lm(formula = pRIF_RpPlus ~ THI_cat + age + hearThresh + DASS_A + DASS_D + DASS_S + RRS, data = efit)
rp_plus_lm_tidy <- tidy(rp_plus_lm) %>% 
  mutate(model = "RpPlus")

rp_min_lm <- lm(formula = pRIF_RpMinus ~ THI_cat + age + hearThresh + DASS_A + DASS_D + DASS_S+ RRS, data = efit)
rp_min_lm_tidy <- tidy(rp_min_lm) %>% 
  mutate(model = "RpMinus")

rp_np_lm <- lm(formula = pRIF_Np ~ THI_cat + age + hearThresh + DASS_A + DASS_D + DASS_S +RRS, data = efit)
rp_np_lm_tidy <- tidy(rp_np_lm) %>% 
  mutate(model = "Np")

RIF_lms <- rbind.data.frame(rp_plus_lm_tidy, rp_min_lm_tidy, rp_np_lm_tidy)

```
#
table RIF linear models
`r knitr::kable(RIF_lms, digits = 2)`

```{r rstanarm RIF elements THI groups lm}
bayes_RIF_RpPlus_lm_tincats <- stan_glm(formula = pRIF_RpPlus ~ THI_cat + age + hearThresh + DASS_A + DASS_D + DASS_S + RRS, data = efit, seed = 12345)#fit standard model

prior_summary(bayes_RIF_RpPlus_lm_tincats)#priors used for this model

summary_bayes_RIF_RpPlus_lm_tincats <- summary(bayes_RIF_RpPlus_lm_tincats) 

summary_bayes_RIF_RpPlus_lm_tincats<- as.data.frame(summary(bayes_RIF_RpPlus_lm_tincats))

summary_bayes_RIF_RpPlus_lm_tincats <- summary_bayes_RIF_RpPlus_lm_tincats %>%
  rownames_to_column(var = "IV")

rank_bayes_RIF_RpPlus_lm_tincats<- summary_bayes_RIF_RpPlus_lm_tincats %>% 
  filter(IV == "THI_cat2"|
         IV == "THI_cat3"|
         IV == "age"|
         IV == "hearThresh"|
         IV == "DASS_A"|
         IV == "DASS_D"|
         IV == "DASS_S" |
           IV == "RRS") %>% 
  mutate(partial_beta_rank = rank(mean),
         task = "RIF_RpPlus") %>% 
  select(task,IV,mean, partial_beta_rank)

rank_bayes_RIF_RpPlus_lm_tincats$mean <- round(rank_bayes_RIF_RpPlus_lm_tincats$mean, digits = 2)

RIF_RpPlus_posterior_samples <- spread_draws(bayes_RIF_RpPlus_lm_tincats, c(THI_cat3, THI_cat2), seed = 123)

RIF_RpPlus_beta_prob_tinnitus <- mean(RIF_RpPlus_posterior_samples$THI_cat2 < 0) %>% round(digits = 2)

RIF_RpPlus_beta_prob_bothersome_tinnitus <- mean(RIF_RpPlus_posterior_samples$THI_cat3 < 0) %>% round(digits = 2)

# same as above for RpMinus
bayes_RIF_RpMinus_lm_tincats <- stan_glm(formula = pRIF_RpMinus ~ THI_cat + age + hearThresh + DASS_A + DASS_D + DASS_S + RRS, data = efit, seed = 12345)#fit standard model

prior_summary(bayes_RIF_RpMinus_lm_tincats)#priors used for this model

summary_bayes_RIF_RpMinus_lm_tincats <- summary(bayes_RIF_RpMinus_lm_tincats) 

summary_bayes_RIF_RpMinus_lm_tincats<- as.data.frame(summary(bayes_RIF_RpMinus_lm_tincats))

summary_bayes_RIF_RpMinus_lm_tincats <- summary_bayes_RIF_RpMinus_lm_tincats %>%
  rownames_to_column(var = "IV")

rank_bayes_RIF_RpMinus_lm_tincats<- summary_bayes_RIF_RpMinus_lm_tincats %>% 
  filter(IV == "THI_cat2"|
         IV == "THI_cat3"|
         IV == "age"|
         IV == "hearThresh"|
         IV == "DASS_A"|
         IV == "DASS_D"|
         IV == "DASS_S" |
           IV == "RRS") %>% 
  mutate(partial_beta_rank = rank(mean),
         task = "RIF_RpMinus") %>% 
  select(task,IV,mean, partial_beta_rank)

rank_bayes_RIF_RpMinus_lm_tincats$mean <- round(rank_bayes_RIF_RpMinus_lm_tincats$mean, digits = 2)

RIF_RpMinus_posterior_samples <- spread_draws(bayes_RIF_RpMinus_lm_tincats, c(THI_cat3, THI_cat2), seed = 123)

RIF_RpMinus_beta_prob_tinnitus <- mean(RIF_RpMinus_posterior_samples$THI_cat2 < 0) %>% round(digits = 2)

RIF_RpMinus_beta_prob_bothersome_tinnitus <- mean(RIF_RpMinus_posterior_samples$THI_cat3 < 0) %>% round(digits = 2)

# same as above for Np
bayes_RIF_Np_lm_tincats <- stan_glm(formula = pRIF_Np ~ THI_cat + age + hearThresh + DASS_A + DASS_D + DASS_S + RRS, data = efit, seed = 12345)#fit standard model

prior_summary(bayes_RIF_Np_lm_tincats)#priors used for this model

summary_bayes_RIF_Np_lm_tincats <- summary(bayes_RIF_Np_lm_tincats) 

summary_bayes_RIF_Np_lm_tincats<- as.data.frame(summary(bayes_RIF_Np_lm_tincats))

summary_bayes_RIF_Np_lm_tincats <- summary_bayes_RIF_Np_lm_tincats %>%
  rownames_to_column(var = "IV")

rank_bayes_RIF_Np_lm_tincats<- summary_bayes_RIF_Np_lm_tincats %>% 
  filter(IV == "THI_cat2"|
         IV == "THI_cat3"|
         IV == "age"|
         IV == "hearThresh"|
         IV == "DASS_A"|
         IV == "DASS_D"|
         IV == "DASS_S" |
           IV == "RRS") %>% 
  mutate(partial_beta_rank = rank(mean),
         task = "RIF_Np") %>% 
  select(task,IV,mean, partial_beta_rank)

rank_bayes_RIF_Np_lm_tincats$mean <- round(rank_bayes_RIF_Np_lm_tincats$mean, digits = 2)

RIF_Np_posterior_samples <- spread_draws(bayes_RIF_Np_lm_tincats, c(THI_cat3, THI_cat2), seed = 123)

RIF_Np_beta_prob_tinnitus <- mean(RIF_Np_posterior_samples$THI_cat2 < 0) %>% round(digits = 2)

RIF_Np_beta_prob_bothersome_tinnitus <- mean(RIF_Np_posterior_samples$THI_cat3 < 0) %>% round(digits = 2)
```

```{r rstanarm RIF elements SCALED THI groups lm}
bayes_RIF_RpPlus_lm_tincats_scaled <- stan_glm(formula = pRIF_RpPlus_scaled ~ THI_cat + age_scaled + hearThresh_scaled + DASS_A_scaled + DASS_D_scaled + DASS_S_scaled + RRS_scaled, data = efit, seed = 12345)#fit standard model

prior_summary(bayes_RIF_RpPlus_lm_tincats_scaled)#priors used for this model

summary_bayes_RIF_RpPlus_lm_tincats_scaled <- summary(bayes_RIF_RpPlus_lm_tincats_scaled) 

summary_bayes_RIF_RpPlus_lm_tincats_scaled<- as.data.frame(summary(bayes_RIF_RpPlus_lm_tincats_scaled))

summary_bayes_RIF_RpPlus_lm_tincats_scaled <- summary_bayes_RIF_RpPlus_lm_tincats_scaled %>%
  rownames_to_column(var = "IV")

rank_bayes_RIF_RpPlus_lm_tincats_scaled<- summary_bayes_RIF_RpPlus_lm_tincats_scaled %>% 
  filter(IV == "THI_cat2"|
         IV == "THI_cat3"|
         IV == "age_scaled"|
         IV == "hearThresh_scaled"|
         IV == "DASS_scaled"|
         IV == "DASS_D_scaled"|
         IV == "DASS_S_scaled" |
           IV == "RRS_scaled") %>% 
  mutate(partial_beta_rank = rank(mean),
         task = "RIF_RpPlus") %>% 
  select(task,IV,mean, partial_beta_rank)

rank_bayes_RIF_RpPlus_lm_tincats_scaled$mean <- round(rank_bayes_RIF_RpPlus_lm_tincats_scaled$mean, digits = 2)

RIF_RpPlus_scaled_posterior_samples <- spread_draws(bayes_RIF_RpPlus_lm_tincats_scaled, c(THI_cat3, THI_cat2, RRS_scaled), seed = 123)

RIF_RpPlus_partial_beta_prob_tinnitus <- mean(RIF_RpPlus_scaled_posterior_samples$THI_cat2 < 0) %>% round(digits = 2)

RIF_RpPlus_partial_beta_prob_bothersome_tinnitus <- mean(RIF_RpPlus_scaled_posterior_samples$THI_cat3 < 0) %>% round(digits = 2)

RIF_RpPlus_partial_beta_prob_RRS_scaled <- mean(RIF_RpPlus_scaled_posterior_samples$RRS_scaled < 0) %>% round(digits = 2)

# same as above for RpMinus
bayes_RIF_RpMinus_lm_tincats_scaled <- stan_glm(formula = pRIF_RpMinus_scaled ~ THI_cat + age_scaled + hearThresh_scaled + DASS_A_scaled + DASS_D_scaled + DASS_S_scaled + RRS_scaled, data = efit, seed = 12345)#fit standard model

prior_summary(bayes_RIF_RpMinus_lm_tincats_scaled)#priors used for this model

summary_bayes_RIF_RpMinus_lm_tincats_scaled <- summary(bayes_RIF_RpMinus_lm_tincats_scaled) 

summary_bayes_RIF_RpMinus_lm_tincats_scaled<- as.data.frame(summary(bayes_RIF_RpMinus_lm_tincats_scaled))

summary_bayes_RIF_RpMinus_lm_tincats_scaled <- summary_bayes_RIF_RpMinus_lm_tincats_scaled %>%
  rownames_to_column(var = "IV")

rank_bayes_RIF_RpMinus_lm_tincats_scaled<- summary_bayes_RIF_RpMinus_lm_tincats_scaled %>% 
  filter(IV == "THI_cat2"|
         IV == "THI_cat3"|
         IV == "age_scaled"|
         IV == "hearThresh_scaled"|
         IV == "DASS_scaled"|
         IV == "DASS_D_scaled"|
         IV == "DASS_S_scaled" |
           IV == "RRS_scaled") %>% 
  mutate(partial_beta_rank = rank(mean),
         task = "RIF_RpMinus") %>% 
  select(task,IV,mean, partial_beta_rank)

rank_bayes_RIF_RpMinus_lm_tincats_scaled$mean <- round(rank_bayes_RIF_RpMinus_lm_tincats_scaled$mean, digits = 2)

RIF_RpMinus_scaled_posterior_samples <- spread_draws(bayes_RIF_RpMinus_lm_tincats_scaled, c(THI_cat3, THI_cat2, RRS_scaled), seed = 123)

RIF_RpMinus_partial_beta_prob_tinnitus <- mean(RIF_RpMinus_scaled_posterior_samples$THI_cat2 < 0) %>% round(digits = 2)

RIF_RpMinus_partial_beta_prob_bothersome_tinnitus <- mean(RIF_RpMinus_scaled_posterior_samples$THI_cat3 < 0) %>% round(digits = 2)

RIF_RpMinus_partial_beta_prob_RRS_scaled <- mean(RIF_RpMinus_scaled_posterior_samples$RRS_scaled < 0) %>% round(digits = 2)

# same as above for Np
bayes_RIF_Np_lm_tincats_scaled <- stan_glm(formula = pRIF_Np_scaled ~ THI_cat + age_scaled + hearThresh_scaled + DASS_A_scaled + DASS_D_scaled + DASS_S_scaled + RRS_scaled, data = efit, seed = 12345)#fit standard model

prior_summary(bayes_RIF_Np_lm_tincats_scaled)#priors used for this model

summary_bayes_RIF_Np_lm_tincats_scaled <- summary(bayes_RIF_Np_lm_tincats_scaled) 

summary_bayes_RIF_Np_lm_tincats_scaled<- as.data.frame(summary(bayes_RIF_Np_lm_tincats_scaled))

summary_bayes_RIF_Np_lm_tincats_scaled <- summary_bayes_RIF_Np_lm_tincats_scaled %>%
  rownames_to_column(var = "IV")

rank_bayes_RIF_Np_lm_tincats_scaled<- summary_bayes_RIF_Np_lm_tincats_scaled %>% 
  filter(IV == "THI_cat2"|
         IV == "THI_cat3"|
         IV == "age_scaled"|
         IV == "hearThresh_scaled"|
         IV == "DASS_scaled"|
         IV == "DASS_D_scaled"|
         IV == "DASS_S_scaled" |
           IV == "RRS_scaled") %>% 
  mutate(partial_beta_rank = rank(mean),
         task = "RIF_Np") %>% 
  select(task,IV,mean, partial_beta_rank)

rank_bayes_RIF_Np_lm_tincats_scaled$mean <- round(rank_bayes_RIF_Np_lm_tincats_scaled$mean, digits = 2)

RIF_Np_scaled_posterior_samples <- spread_draws(bayes_RIF_Np_lm_tincats_scaled, c(THI_cat3, THI_cat2, RRS_scaled), seed = 123)

RIF_Np_partial_beta_prob_tinnitus <- mean(RIF_Np_scaled_posterior_samples$THI_cat2 < 0) %>% round(digits = 2)

RIF_Np_partial_beta_prob_bothersome_tinnitus <- mean(RIF_Np_scaled_posterior_samples$THI_cat3 < 0) %>% round(digits = 2)

RIF_Np_partial_beta_prob_RRS_scaled <- mean(RIF_Np_scaled_posterior_samples$RRS_scaled < 0) %>% round(digits = 2)

#create scaled beta bayes table for all models

bayesRIFcat_lmtable <- rbind(rank_bayes_RIF_RpPlus_lm_tincats_scaled,
      rank_bayes_RIF_RpMinus_lm_tincats_scaled,
      rank_bayes_RIF_Np_lm_tincats_scaled)
```
#
bayes RIF category full GLM table

`r knitr::kable(bayesRIFcat_lmtable)`
```{r create table of RRS estimates and non-zero probs for beta tinnitus groups}
RRS_partial_beta_table <- rbind.data.frame(rank_bayes_RIF_RpPlus_lm_tincats_scaled, rank_bayes_RIF_RpMinus_lm_tincats_scaled, rank_bayes_RIF_Np_lm_tincats_scaled) %>% 
  filter(IV == "RRS_scaled") %>% 
  mutate(less_non_zero_prob = c(
    RIF_RpPlus_partial_beta_prob_RRS_scaled,
    RIF_RpMinus_partial_beta_prob_RRS_scaled,
    RIF_Np_partial_beta_prob_RRS_scaled),
    more_non_zero_prob = 1-less_non_zero_prob)


RRS_partial_beta_table <-  RRS_partial_beta_table %>%  select(-IV)#create RRS coefficient table


tin_RIF_table_plus <- rank_bayes_RIF_RpPlus_lm_tincats %>% 
  filter(IV == "THI_cat2" | IV == "THI_cat3")

tin_RIF_table_minus <- rank_bayes_RIF_RpMinus_lm_tincats %>% 
  filter(IV == "THI_cat2" | IV == "THI_cat3")

tin_RIF_table_Np <- rank_bayes_RIF_Np_lm_tincats %>% 
  filter(IV == "THI_cat2" | IV == "THI_cat3")

all_tin_RIF_table <- rbind(tin_RIF_table_plus, tin_RIF_table_minus, tin_RIF_table_Np) 


all_tin_RIF_table$IV <- recode(all_tin_RIF_table$IV, THI_cat2 = "tinnitus", THI_cat3 = "bothersome tinnitus")

all_tin_RIF_table <- all_tin_RIF_table %>% mutate(less_non_zero_prob = c(
  RIF_RpPlus_beta_prob_tinnitus,
    RIF_RpPlus_beta_prob_bothersome_tinnitus,
    RIF_RpMinus_beta_prob_tinnitus, 
    RIF_RpMinus_beta_prob_bothersome_tinnitus,
    RIF_Np_beta_prob_tinnitus,
    RIF_Np_beta_prob_bothersome_tinnitus
  ),
  more_non_zero_prob = 1-less_non_zero_prob)

```
#
RRS partial betas
`r knitr::kable(RRS_partial_beta_table)`

#
RIF tinnitus and bothersome tinnitus coefficients and beta-probabilities
`r knitr::kable(all_tin_RIF_table)`

#BAYESIAN LINEAR MODELS

##Number-letter sequencing
```{r rstanarm nls THI groups lm}
bayes_nls_lm_tincats <- stan_glm(formula = nls_correct ~ THI_cat + age + hearThresh + DASS_A + DASS_D + DASS_S, data = efit, seed = 12345)#fit standard model

prior_summary(bayes_nls_lm_tincats)#priors used for this model

summary_bayes_nls_lm_tincats <- summary(bayes_nls_lm_tincats) 


#standardised version of the model
bayes_nls_lm_tincats_scaled <- stan_glm(formula = nls_correct_scaled ~ THI_cat + age_scaled + hearThresh_scaled + DASS_A_scaled + DASS_D_scaled + DASS_S_scaled, data = efit, seed = 12345)

summary_bayes_nls_lm_tincats_scaled <- as.data.frame(summary(bayes_nls_lm_tincats_scaled))

summary_bayes_nls_lm_tincats_scaled <- summary_bayes_nls_lm_tincats_scaled %>%
  rownames_to_column(var = "IV")

rank_bayes_nls_lm_tincats_scaled <- summary_bayes_nls_lm_tincats_scaled %>% 
  filter(IV == "THI_cat2"|
         IV == "THI_cat3"|
         IV == "age_scaled"|
         IV == "hearThresh_scaled"|
         IV == "DASS_A_scaled"|
         IV == "DASS_D_scaled"|
         IV == "DASS_S_scaled") %>% 
  mutate(partial_beta_rank = rank(mean),
         task = "nls_correct") %>% 
  select(task,IV,mean, partial_beta_rank)

rank_bayes_nls_lm_tincats_scaled$mean <- round(rank_bayes_nls_lm_tincats_scaled$mean, digits = 2)

nls_scaled_posterior_samples <- spread_draws(bayes_nls_lm_tincats_scaled, c(THI_cat3, THI_cat2), seed = 123)

nls_partial_beta_prob_tinnitus <- mean(nls_scaled_posterior_samples$THI_cat2 < 0) %>% round(digits = 2)

nls_partial_beta_prob_bothersome_tinnitus <- mean(nls_scaled_posterior_samples$THI_cat3 < 0) %>% round(digits = 2)

#posterior_samples <- as.matrix(bayes_nls_lm_tincats, pars = "THI_cat3")#extract posterior draws for THI_cat3

#mean(posterior_samples2$THI_cat3 < 0)#tells us the model's probability that draws for this paramater are < 0
```

##Keep track
```{r rstanarm keep track THI groups lm}
bayes_keepTrack_lm_tincats <- stan_glm(formula = keepTrack ~ THI_cat + age + hearThresh + DASS_A + DASS_D + DASS_S, data = efit, seed = 12345)#fit standard model

prior_summary(bayes_keepTrack_lm_tincats)#priors used for this model

summary_bayes_keepTrack_lm_tincats <- summary(bayes_keepTrack_lm_tincats) 


#standardised version of the model
bayes_keepTrack_lm_tincats_scaled <- stan_glm(formula = keepTrack_scaled ~ THI_cat + age_scaled + hearThresh_scaled + DASS_A_scaled + DASS_D_scaled + DASS_S_scaled, data = efit, seed = 12345)

summary_bayes_keepTrack_lm_tincats_scaled <- as.data.frame(summary(bayes_keepTrack_lm_tincats_scaled))

summary_bayes_keepTrack_lm_tincats_scaled <- summary_bayes_keepTrack_lm_tincats_scaled %>%
  rownames_to_column(var = "IV")

rank_bayes_keepTrack_lm_tincats_scaled <- summary_bayes_keepTrack_lm_tincats_scaled %>% 
  filter(IV == "THI_cat2"|
         IV == "THI_cat3"|
         IV == "age_scaled"|
         IV == "hearThresh_scaled"|
         IV == "DASS_A_scaled"|
         IV == "DASS_D_scaled"|
         IV == "DASS_S_scaled") %>% 
  mutate(partial_beta_rank = rank(mean),
         task = "keep_track_correct") %>% 
  select(task, IV,mean, partial_beta_rank)

rank_bayes_keepTrack_lm_tincats_scaled$mean <- round(rank_bayes_keepTrack_lm_tincats_scaled$mean, digits = 2)

keepTrack_scaled_posterior_samples <- spread_draws(bayes_keepTrack_lm_tincats_scaled, c(THI_cat3, THI_cat2), seed = 123)

keepTrack_partial_beta_prob_tinnitus <- mean(keepTrack_scaled_posterior_samples$THI_cat2 < 0) %>% round(digits = 2)

keepTrack_partial_beta_prob_bothersome_tinnitus <- mean(keepTrack_scaled_posterior_samples$THI_cat3 < 0) %>% round(digits = 2)

#posterior_samples <- as.matrix(bayes_nls_lm_tincats, pars = "THI_cat3")#extract posterior draws for THI_cat3
```

##Stroop
###RT
```{r rstanarm stroop_incong rt THI groups lm}
bayes_stroopRT_lm_tincats <- stan_glm(formula = stroop_incongruent ~ THI_cat + age + hearThresh + DASS_A + DASS_D + DASS_S, data = efit, seed = 12345)#fit standard model

prior_summary(bayes_stroopRT_lm_tincats)#priors used for this model

summary_bayes_stroopRT_lm_tincats <- summary(bayes_stroopRT_lm_tincats) 


#standardised version of the model
bayes_stroopRT_lm_tincats_scaled <- stan_glm(formula = stroop_incongruent_scaled ~ THI_cat + age_scaled + hearThresh_scaled + DASS_A_scaled + DASS_D_scaled + DASS_S_scaled, data = efit, seed = 12345)

summary_bayes_stroopRT_lm_tincats_scaled <- as.data.frame(summary(bayes_stroopRT_lm_tincats_scaled))

summary_bayes_stroopRT_lm_tincats_scaled <- summary_bayes_stroopRT_lm_tincats_scaled %>%
  rownames_to_column(var = "IV")

rank_bayes_stroopRT_lm_tincats_scaled <- summary_bayes_stroopRT_lm_tincats_scaled %>% 
  filter(IV == "THI_cat2"|
         IV == "THI_cat3"|
         IV == "age_scaled"|
         IV == "hearThresh_scaled"|
         IV == "DASS_A_scaled"|
         IV == "DASS_D_scaled"|
         IV == "DASS_S_scaled") %>% 
  mutate(partial_beta_rank = rank(-mean),
         task = "stroop_rt") %>% 
  select(task,IV,mean, partial_beta_rank)#USE -mean() for rt and errors

rank_bayes_stroopRT_lm_tincats_scaled$mean <- round(rank_bayes_stroopRT_lm_tincats_scaled$mean, digits = 2)

stroopRT_scaled_posterior_samples <- spread_draws(bayes_stroopRT_lm_tincats_scaled, c(THI_cat3, THI_cat2), seed = 123)

stroopRT_partial_beta_prob_tinnitus <- mean(stroopRT_scaled_posterior_samples$THI_cat2 < 0) %>% round(digits = 2)

stroopRT_partial_beta_prob_bothersome_tinnitus <- mean(stroopRT_scaled_posterior_samples$THI_cat3 < 0) %>% round(digits = 2)

#posterior_samples <- as.matrix(bayes_nls_lm_tincats, pars = "THI_cat3")#extract posterior draws for THI_cat3
```

###Errors
```{r rstanarm stroop error THI groups lm}
bayes_stroopErr_lm_tincats <- stan_glm(formula = stroop_errors ~ THI_cat + age + hearThresh + DASS_A + DASS_D + DASS_S, data = efit,seed = 12345)#fit standard model

prior_summary(bayes_stroopErr_lm_tincats)#priors used for this model

summary_bayes_stroopErr_lm_tincats <- summary(bayes_stroopErr_lm_tincats) 


#standardised version of the model
bayes_stroopErr_lm_tincats_scaled <- stan_glm(formula = stroop_errors_scaled ~ THI_cat + age_scaled + hearThresh_scaled + DASS_A_scaled + DASS_D_scaled + DASS_S_scaled, data = efit, seed = 12345)

summary_bayes_stroopErr_lm_tincats_scaled <- as.data.frame(summary(bayes_stroopErr_lm_tincats_scaled))

summary_bayes_stroopErr_lm_tincats_scaled <- summary_bayes_stroopErr_lm_tincats_scaled %>%
  rownames_to_column(var = "IV")

rank_bayes_stroopErr_lm_tincats_scaled <- summary_bayes_stroopErr_lm_tincats_scaled %>% 
  filter(IV == "THI_cat2"|
         IV == "THI_cat3"|
         IV == "age_scaled"|
         IV == "hearThresh_scaled"|
         IV == "DASS_A_scaled"|
         IV == "DASS_D_scaled"|
         IV == "DASS_S_scaled") %>% 
  mutate(partial_beta_rank = rank(-mean),
         task = "stroop_errors") %>% 
  select(task,IV,mean, partial_beta_rank)#USE -mean() for rt and errors

rank_bayes_stroopErr_lm_tincats_scaled$mean <- round(rank_bayes_stroopErr_lm_tincats_scaled$mean, digits = 2)

stroopErr_scaled_posterior_samples <- spread_draws(bayes_stroopErr_lm_tincats_scaled, c(THI_cat3, THI_cat2), seed = 123)

stroopErr_partial_beta_prob_tinnitus <- mean(stroopErr_scaled_posterior_samples$THI_cat2 < 0) %>% round(digits = 2)

stroopErr_partial_beta_prob_bothersome_tinnitus <- mean(stroopErr_scaled_posterior_samples$THI_cat3 < 0) %>% round(digits = 2)

#posterior_samples <- as.matrix(bayes_nls_lm_tincats, pars = "THI_cat3")#extract posterior draws for THI_cat3
```

##RIF effect
```{r rstanarm RIF_Diff error THI groups lm}
bayes_RIF_Diff_lm_tincats <- stan_glm(formula = RIF_Diff ~ THI_cat + age + hearThresh + DASS_A + DASS_D + DASS_S, data = efit, seed = 12345)#fit standard model

prior_summary(bayes_RIF_Diff_lm_tincats)#priors used for this model

summary_bayes_RIF_Diff_lm_tincats <- summary(bayes_RIF_Diff_lm_tincats) 


#standardised version of the model
bayes_RIF_Diff_lm_tincats_scaled <- stan_glm(formula = RIF_Diff_scaled ~ THI_cat + age_scaled + hearThresh_scaled + DASS_A_scaled + DASS_D_scaled + DASS_S_scaled, data = efit,seed = 12345)

summary_bayes_RIF_Diff_lm_tincats_scaled <- as.data.frame(summary(bayes_RIF_Diff_lm_tincats_scaled))

summary_bayes_RIF_Diff_lm_tincats_scaled <- summary_bayes_RIF_Diff_lm_tincats_scaled %>%
  rownames_to_column(var = "IV")

rank_bayes_RIF_Diff_lm_tincats_scaled <- summary_bayes_RIF_Diff_lm_tincats_scaled %>% 
  filter(IV == "THI_cat2"|
         IV == "THI_cat3"|
         IV == "age_scaled"|
         IV == "hearThresh_scaled"|
         IV == "DASS_A_scaled"|
         IV == "DASS_D_scaled"|
         IV == "DASS_S_scaled") %>% 
  mutate(partial_beta_rank = rank(mean),
         task = "RIF_effect") %>% 
  select(task, IV,mean, partial_beta_rank)

rank_bayes_RIF_Diff_lm_tincats_scaled$mean <- round(rank_bayes_RIF_Diff_lm_tincats_scaled$mean, digits = 2)

RIF_Diff_scaled_posterior_samples <- spread_draws(bayes_RIF_Diff_lm_tincats_scaled, c(THI_cat3, THI_cat2), seed = 123)

RIF_Diff_partial_beta_prob_tinnitus <- mean(RIF_Diff_scaled_posterior_samples$THI_cat2 < 0) %>% round(digits = 2)

RIF_Diff_partial_beta_prob_bothersome_tinnitus <- mean(RIF_Diff_scaled_posterior_samples$THI_cat3 < 0) %>% round(digits = 2)

#posterior_samples <- as.matrix(bayes_nls_lm_tincats, pars = "THI_cat3")#extract posterior draws for THI_cat3
```

##Rule switch
###RT
```{r rstanarm switch_cost rt THI groups lm}
bayes_switchCost_lm_tincats <- stan_glm(formula = switch_cost ~ THI_cat + age + hearThresh + DASS_A + DASS_D + DASS_S, data = efit, seed = 12345)#fit standard model

prior_summary(bayes_switchCost_lm_tincats)#priors used for this model

summary_bayes_switchCost_lm_tincats <- summary(bayes_switchCost_lm_tincats) 


#standardised version of the model
bayes_switchCost_lm_tincats_scaled <- stan_glm(formula = switch_cost_scaled ~ THI_cat + age_scaled + hearThresh_scaled + DASS_A_scaled + DASS_D_scaled + DASS_S_scaled, data = efit, seed = 12345)

summary_bayes_switchCost_lm_tincats_scaled <- as.data.frame(summary(bayes_switchCost_lm_tincats_scaled))

summary_bayes_switchCost_lm_tincats_scaled <- summary_bayes_switchCost_lm_tincats_scaled %>%
  rownames_to_column(var = "IV")

rank_bayes_switchCost_lm_tincats_scaled <- summary_bayes_switchCost_lm_tincats_scaled %>% 
  filter(IV == "THI_cat2"|
         IV == "THI_cat3"|
         IV == "age_scaled"|
         IV == "hearThresh_scaled"|
         IV == "DASS_A_scaled"|
         IV == "DASS_D_scaled"|
         IV == "DASS_S_scaled") %>% 
  mutate(partial_beta_rank = rank(-mean),
         task = "switch_cost") %>% 
  select(task, IV,mean, partial_beta_rank)#USE -mean() for rt and errors

rank_bayes_switchCost_lm_tincats_scaled$mean <- round(rank_bayes_switchCost_lm_tincats_scaled$mean, digits = 2)

switchCost_scaled_posterior_samples <- spread_draws(bayes_switchCost_lm_tincats_scaled, c(THI_cat3, THI_cat2), seed = 123)

switchCost_partial_beta_prob_tinnitus <- mean(switchCost_scaled_posterior_samples$THI_cat2 < 0) %>% round(digits = 2)

switchCost_partial_beta_prob_bothersome_tinnitus <- mean(switchCost_scaled_posterior_samples$THI_cat3 < 0) %>% round(digits = 2)

#posterior_samples <- as.matrix(bayes_nls_lm_tincats, pars = "THI_cat3")#extract posterior draws for THI_cat3
```

###Errors
```{r rstanarm rule errors THI groups lm}
bayes_ruleErr_lm_tincats <- stan_glm(formula = rule_errors ~ THI_cat + age + hearThresh + DASS_A + DASS_D + DASS_S, data = efit, seed = 12345)#fit standard model

prior_summary(bayes_ruleErr_lm_tincats)#priors used for this model

summary_bayes_ruleErr_lm_tincats <- summary(bayes_ruleErr_lm_tincats) 


#standardised version of the model
bayes_ruleErr_lm_tincats_scaled <- stan_glm(formula = rule_errors_scaled ~ THI_cat + age_scaled + hearThresh_scaled + DASS_A_scaled + DASS_D_scaled + DASS_S_scaled, data = efit, seed = 12345)

summary_bayes_ruleErr_lm_tincats_scaled <- as.data.frame(summary(bayes_ruleErr_lm_tincats_scaled))

summary_bayes_ruleErr_lm_tincats_scaled <- summary_bayes_ruleErr_lm_tincats_scaled %>%
  rownames_to_column(var = "IV")

rank_bayes_ruleErr_lm_tincats_scaled <- summary_bayes_ruleErr_lm_tincats_scaled %>% 
  filter(IV == "THI_cat2"|
         IV == "THI_cat3"|
         IV == "age_scaled"|
         IV == "hearThresh_scaled"|
         IV == "DASS_A_scaled"|
         IV == "DASS_D_scaled"|
         IV == "DASS_S_scaled") %>% 
  mutate(partial_beta_rank = rank(-mean),
         task = "rule_errors") %>% 
  select(task, IV,mean, partial_beta_rank)#USE -mean() for rt and errors

rank_bayes_ruleErr_lm_tincats_scaled$mean <- round(rank_bayes_ruleErr_lm_tincats_scaled$mean, digits = 2)

ruleErr_scaled_posterior_samples <- spread_draws(bayes_ruleErr_lm_tincats_scaled, c(THI_cat3, THI_cat2), seed = 123)

ruleErr_partial_beta_prob_tinnitus <- mean(ruleErr_scaled_posterior_samples$THI_cat2 < 0) %>% round(digits = 2)

ruleErr_partial_beta_prob_bothersome_tinnitus <- mean(ruleErr_scaled_posterior_samples$THI_cat3 < 0) %>% round(digits = 2)

#posterior_samples <- as.matrix(bayes_nls_lm_tincats, pars = "THI_cat3")#extract posterior draws for THI_cat3
```

##Dual task
```{r rstanarm Dualtask_Diff error THI groups lm}
bayes_dualTask_lm_tincats <- stan_glm(formula = dual_task_total ~ THI_cat + age + hearThresh + DASS_A + DASS_D + DASS_S, data = efit, seed = 12345)#fit standard model

prior_summary(bayes_dualTask_lm_tincats)#priors used for this model

summary_bayes_dualTask_lm_tincats <- summary(bayes_dualTask_lm_tincats) 


#standardised version of the model
bayes_dualTask_lm_tincats_scaled <- stan_glm(formula = dual_task_total_scaled ~ THI_cat + age_scaled + hearThresh_scaled + DASS_A_scaled + DASS_D_scaled + DASS_S_scaled, data = efit, seed = 12345)

summary_bayes_dualTask_lm_tincats_scaled <- as.data.frame(summary(bayes_dualTask_lm_tincats_scaled))

summary_bayes_dualTask_lm_tincats_scaled <- summary_bayes_dualTask_lm_tincats_scaled %>%
  rownames_to_column(var = "IV")

rank_bayes_dualTask_lm_tincats_scaled <- summary_bayes_dualTask_lm_tincats_scaled %>% 
  filter(IV == "THI_cat2"|
         IV == "THI_cat3"|
         IV == "age_scaled"|
         IV == "hearThresh_scaled"|
         IV == "DASS_A_scaled"|
         IV == "DASS_D_scaled"|
         IV == "DASS_S_scaled") %>% 
  mutate(partial_beta_rank = rank(mean),
         task = "dual_task_words_correct") %>% 
  select(task, IV,mean, partial_beta_rank)

rank_bayes_dualTask_lm_tincats_scaled$mean <- round(rank_bayes_dualTask_lm_tincats_scaled$mean, digits = 2)

dualTask_scaled_posterior_samples <- spread_draws(bayes_dualTask_lm_tincats_scaled, c(THI_cat3, THI_cat2), seed = 123)

dualTask_partial_beta_prob_tinnitus <- mean(dualTask_scaled_posterior_samples$THI_cat2 < 0) %>% round(digits = 2)

dualTask_partial_beta_prob_bothersome_tinnitus <- mean(dualTask_scaled_posterior_samples$THI_cat3 < 0) %>% round(digits = 2)

#posterior_samples <- as.matrix(bayes_nls_lm_tincats, pars = "THI_cat3")#extract posterior draws for THI_cat3
```

##Matrix reasoning
```{r rstanarm matrix reason THI groups lm}
bayes_matrixReason_lm_tincats <- stan_glm(formula = matrixReason ~ THI_cat + age + hearThresh + DASS_A + DASS_D + DASS_S, data = efit, seed = 12345)#fit standard model

prior_summary(bayes_matrixReason_lm_tincats)#priors used for this model

summary_bayes_matrixReason_lm_tincats <- summary(bayes_matrixReason_lm_tincats) 


#standardised version of the model
bayes_matrixReason_lm_tincats_scaled <- stan_glm(formula = matrixReason_scaled ~ THI_cat + age_scaled + hearThresh_scaled + DASS_A_scaled + DASS_D_scaled + DASS_S_scaled, data = efit,seed = 12345)

summary_bayes_matrixReason_lm_tincats_scaled <- as.data.frame(summary(bayes_matrixReason_lm_tincats_scaled))

summary_bayes_matrixReason_lm_tincats_scaled <- summary_bayes_matrixReason_lm_tincats_scaled %>%
  rownames_to_column(var = "IV")

rank_bayes_matrixReason_lm_tincats_scaled <- summary_bayes_matrixReason_lm_tincats_scaled %>% 
  filter(IV == "THI_cat2"|
         IV == "THI_cat3"|
         IV == "age_scaled"|
         IV == "hearThresh_scaled"|
         IV == "DASS_A_scaled"|
         IV == "DASS_D_scaled"|
         IV == "DASS_S_scaled") %>% 
  mutate(partial_beta_rank = rank(mean),
         task = "matrix_reasoning") %>% 
  select(task, IV,mean, partial_beta_rank)

rank_bayes_matrixReason_lm_tincats_scaled$mean <- round(rank_bayes_matrixReason_lm_tincats_scaled$mean, digits = 2)

matrixReason_scaled_posterior_samples <- spread_draws(bayes_matrixReason_lm_tincats_scaled, c(THI_cat3, THI_cat2), seed = 123)

matrixReason_partial_beta_prob_tinnitus <- mean(matrixReason_scaled_posterior_samples$THI_cat2 < 0) %>% round(digits = 2)

matrixReason_partial_beta_prob_bothersome_tinnitus <- mean(matrixReason_scaled_posterior_samples$THI_cat3 < 0) %>% round(digits = 2)

#posterior_samples <- as.matrix(bayes_nls_lm_tincats, pars = "THI_cat3")#extract posterior draws for THI_cat3
```

```{r bind tables of all ranked bayes lm results}
all_bayes_ranked_lm_tincats_scaled <- rbind(
  rank_bayes_nls_lm_tincats_scaled,
  rank_bayes_dualTask_lm_tincats_scaled,
  rank_bayes_keepTrack_lm_tincats_scaled,
 rank_bayes_matrixReason_lm_tincats_scaled,
  rank_bayes_RIF_Diff_lm_tincats_scaled,
  rank_bayes_ruleErr_lm_tincats_scaled,
  rank_bayes_switchCost_lm_tincats_scaled,
  rank_bayes_stroopErr_lm_tincats_scaled,
  rank_bayes_stroopRT_lm_tincats_scaled
) %>% rename(estimate = mean)

all_bayes_ranked_lm_tincats_scaled$IV <- all_bayes_ranked_lm_tincats_scaled$IV %>% 
  str_replace("THI_cat2", "tinnitus") %>% 
  str_replace("THI_cat3", "bothersome_tinnitus")

```

```{r ratio of beta weights for bothersome tinnitus and tinnitus}
#make a vector of all the bothersome tinnitus beta weights
both_vec <- c(rep(all_bayes_ranked_lm_tincats_scaled[2,3], 7),
  rep(all_bayes_ranked_lm_tincats_scaled[9,3], 7),
  rep(all_bayes_ranked_lm_tincats_scaled[16,3], 7),
  rep(all_bayes_ranked_lm_tincats_scaled[23,3], 7),
  rep(all_bayes_ranked_lm_tincats_scaled[30,3], 7),
  rep(all_bayes_ranked_lm_tincats_scaled[37,3], 7),
  rep(all_bayes_ranked_lm_tincats_scaled[44,3], 7),
  rep(all_bayes_ranked_lm_tincats_scaled[51,3], 7),
  rep(all_bayes_ranked_lm_tincats_scaled[58,3], 7))

#mutate to ratios by vector dividing estimate column 

bothersome_beta_ratio <- all_bayes_ranked_lm_tincats_scaled %>% 
      mutate(bothersome_vector = both_vec,
        bother_greater_beta_ratio = both_vec/estimate,
        bother_worse_beta_ratio = estimate/both_vec) %>% 
  select(task,IV,
         bothersome_vector, 
         estimate, 
         bother_greater_beta_ratio,
         bother_worse_beta_ratio) %>% 
  arrange(IV, 
          desc(bother_greater_beta_ratio),
          desc(bother_worse_beta_ratio)) %>% 
  filter(IV != "bothersome_tinnitus")#,
         #bother_beta_ratio > 2 | bother_beta_ratio < -2)
#filtered to beta ratios where the x2 difference between bothersome tinnitus
```
#
bothersome beta ratios
`r knitr::kable(bothersome_beta_ratio, digits = 2)`

```{r find bayes ranks of bothersome tinnitus partial beta}
#table of probability estimate that coefficient representes poor performance for bothersome tinnitus
bayes_bothersome_tinnitus_rank <- all_bayes_ranked_lm_tincats_scaled %>%
  filter(IV == "bothersome_tinnitus") %>% 
  select(task, partial_beta_rank, estimate) %>% 
  arrange(task)

bayes_bothersome_tinnitus_rank <- bayes_bothersome_tinnitus_rank %>% 
  mutate(prob_beta_less_than_0 = c(
    dualTask_partial_beta_prob_bothersome_tinnitus,
    keepTrack_partial_beta_prob_bothersome_tinnitus,
    matrixReason_partial_beta_prob_bothersome_tinnitus,
    nls_partial_beta_prob_bothersome_tinnitus,
    RIF_Diff_partial_beta_prob_bothersome_tinnitus,
    ruleErr_partial_beta_prob_bothersome_tinnitus,
    stroopErr_partial_beta_prob_bothersome_tinnitus,
    stroopRT_partial_beta_prob_bothersome_tinnitus,
    switchCost_partial_beta_prob_bothersome_tinnitus)) %>%
  arrange(estimate, partial_beta_rank)

bayes_bothersome_tinnitus_rank <- bayes_bothersome_tinnitus_rank %>% mutate(prob_beta_more_than_0 = 1-prob_beta_less_than_0)

#table of probability estimate that coefficient representes poor performance for tinnitus
bayes_tinnitus_rank <- all_bayes_ranked_lm_tincats_scaled %>%
  filter(IV == "tinnitus") %>% 
  select(task, partial_beta_rank, estimate) %>% 
  arrange(task)

bayes_tinnitus_rank <- bayes_tinnitus_rank %>% 
  mutate(prob_beta_less_than_0 = c(
    dualTask_partial_beta_prob_tinnitus,
    keepTrack_partial_beta_prob_tinnitus,
    matrixReason_partial_beta_prob_tinnitus,
    nls_partial_beta_prob_tinnitus,
    RIF_Diff_partial_beta_prob_tinnitus,
    ruleErr_partial_beta_prob_tinnitus,
    stroopErr_partial_beta_prob_tinnitus,
    stroopRT_partial_beta_prob_tinnitus,
    switchCost_partial_beta_prob_tinnitus)) %>%
  arrange(estimate, partial_beta_rank)

bayes_tinnitus_rank <- bayes_tinnitus_rank %>% mutate(prob_beta_more_than_0 = 1-prob_beta_less_than_0)

```
#
table of bayes bothersome tinnitus rank
`r knitr::kable(bayes_bothersome_tinnitus_rank)`
#
table of bayes tinnitus rank
`r knitr::kable(bayes_tinnitus_rank)`

#SCM modelling
```{r prepare data nm_thesis data}
#load nm thesis data
nm_data <- read_csv("nm_thesis.csv")

nm_data <- nm_data %>% mutate(
    THI_cat = ifelse(
      thi_total >= 38 ,"bothersome tinnitus", "tinnitus")) #add a categorical variable with the groups split by thi_total scores

#count number of bothered and non-bothered
nm_group_count <- nm_data %>% 
  group_by(THI_cat) %>% 
  summarise(total = n())
#create scaled variables for lms
nm_data <- nm_data %>% 
  mutate(thi_total_scaled = scale(thi_total),
         PTA_Better_scaled = scale(PTA_Better),
         WASI_Raw_scaled = scale(WASI_Raw),
         core_total_scaled = scale(core_total))

```

```{r prepare EFiT data}
efit_scm <- efit %>% 
  filter(THI_cat == "tinnitus" | THI_cat == "bothersome tinnitus")#remove control group

efit_scm <- efit_scm %>% 
  mutate(glo_psych = DASS_D + DASS_A + DASS_S)#great global psychological distress variable

efit_scm <- efit_scm %>% 
  mutate(nls_correct_scaled = scale(nls_correct),
         RIF_Diff_scaled = scale(RIF_Diff),
         keepTrack_scaled = scale(keepTrack),
         stroop_incongruent_scaled = scale(stroop_incongruent),
         stroop_errors_scaled = scale(stroop_errors),
         switch_cost_scaled = scale(switch_cost),
         rule_errors_scaled = scale(rule_errors),
         dual_task_total_scaled = scale(dual_task_total),
         matrixReason_scaled = scale(matrixReason),
         age_scaled = scale(age),
         hearThresh_scaled = scale(hearThresh),
         DASS_A_scaled = scale(DASS_A),
         DASS_D_scaled = scale(DASS_D),
         DASS_S_scaled = scale(DASS_S),
         CRIq_scaled = scale(CRIq),
         RRS_scaled = scale(RRS),
         glo_psych_scaled = scale(glo_psych),
         THI_scaled = scale(THI)
  )
```

```{r historgrams THI}
nm_data %>% ggplot(aes(x =thi_total)) +
  geom_histogram()

efit_scm %>% ggplot(aes(x =THI)) +
  geom_histogram()
```

```{r frequentist matrix reason causal models without duration}
#EFiT unscaled model
efit_scm_matrix_lm <- lm(THI ~ glo_psych + matrixReason + hearThresh, data = efit_scm)

#tidy and round model
tidy_efit_scm_matrix_lm <- tidy(efit_scm_matrix_lm) %>% 
  mutate_if(is.numeric, round, 3)

#EFiT scaled model
efit_scm_matrix_lm_scaled <- lm(scale(THI) ~ scale(glo_psych) + scale(matrixReason) + scale(hearThresh), data = efit_scm)

#tidy and round model
tidy_efit_scm_matrix_lm_scaled <- tidy(efit_scm_matrix_lm_scaled) %>% 
  mutate_if(is.numeric, round, 3)

#nm_thesis unscaled model
nm_scm_matrix_lm <- lm(thi_total ~ core_total + WASI_Raw + PTA_Better, data = nm_data)

#tidy and round model
tidy_nm_scm_matrix_lm <- tidy(nm_scm_matrix_lm) %>% 
  mutate_if(is.numeric, round, 3)

#nm_thesis scaled model
nm_scm_matrix_lm_scaled <- lm(thi_total_scaled ~ core_total_scaled+ WASI_Raw_scaled + PTA_Better_scaled, data = nm_data)

#tidy and round model
tidy_nm_scm_matrix_lm_scaled <- tidy(nm_scm_matrix_lm_scaled) %>% 
  mutate_if(is.numeric, round, 3)
```

```{r bayesian matrix reason causal models without duration}
#EFiT unscaled model
efit_scm_matrix_bayes_lm <- stan_glm(THI ~ glo_psych + matrixReason + hearThresh, data = efit_scm, seed = 12345)

#tidy and round model
tidy_efit_scm_matrix_bayes_lm <- tidy(efit_scm_matrix_bayes_lm) %>% 
  mutate_if(is.numeric, round, 3)

#EFiT scaled model
efit_scm_matrix_bayes_lm_scaled <- stan_glm(THI_scaled ~ glo_psych_scaled + matrixReason_scaled + hearThresh_scaled, data = efit_scm)

#tidy and round model
tidy_efit_scm_matrix_bayes_lm_scaled <- tidy(efit_scm_matrix_bayes_lm_scaled) %>% 
  mutate_if(is.numeric, round, 3)

#nm_thesis unscaled model
nm_scm_matrix_bayes_lm <- stan_glm(thi_total ~ core_total + WASI_Raw + PTA_Better, data = nm_data, seed = 12345)

#tidy and round model
tidy_nm_scm_matrix_bayes_lm <- tidy(nm_scm_matrix_bayes_lm) %>% 
  mutate_if(is.numeric, round, 3)

#nm_thesis scaled model
nm_scm_matrix_bayes_lm_scaled <- stan_glm(thi_total_scaled ~ core_total_scaled+ WASI_Raw_scaled + PTA_Better_scaled, data = nm_data, seed = 12345)

#tidy and round model
tidy_nm_scm_matrix_bayes_lm_scaled <- tidy(nm_scm_matrix_bayes_lm_scaled) %>% 
  mutate_if(is.numeric, round, 3)
```

```{r posterior samples for both models}
#draws from efit matrix
efit_scm_matrix_posterior_draws <- spread_draws(efit_scm_matrix_bayes_lm_scaled, matrixReason_scaled, seed = 123)
#probability that coef is < 0
efit_scm_matrix_partial_beta_prob <- mean(efit_scm_matrix_posterior_draws$matrixReason_scaled < 0) %>% round(digits = 2)
#draws from nm matrix model
nm_scm_matrix_posterior_draws <- spread_draws(nm_scm_matrix_bayes_lm_scaled, WASI_Raw_scaled, seed = 123)

nm_scm_matrix_partial_beta_prob <- mean(nm_scm_matrix_posterior_draws$WASI_Raw_scaled < 0) %>% round(digits = 2)
```

```{r nm_data principal axis factor analysis}
#create dateset to reduce
paf_nm_dat <- nm_data %>%  select(WASI_Raw, WCST_CatsCompleted, DSB_Raw)

#sphericity
parameters::check_sphericity(paf_nm_dat)
KMO(paf_nm_dat)
vss(x = paf_nm_dat)
#single factor no roation
nm_paf <- fa(paf_nm_dat, nfactors = 1, fm = "pa", rotate = 'none', covar = FALSE)

fa.diagram(nm_paf)

#single factor 
fa.parallel(paf_nm_dat, fa = "fa", fm = "pa")
#Thurstone is regression scores, cite skrondal 2001, Bartless methods gives the same lm inference
nm_fs <- factor.scores(paf_nm_dat, nm_paf, method = "Thurstone")

nm_factor_score <- nm_fs$scores %>% unlist()
nm_factor_score <- as.data.frame(nm_factor_score)

nm_factor_score <- nm_factor_score$PA1
#bind factor scores to 
nm_data <- cbind(nm_factor_score, nm_data)

nm_scm_fsr <- lm(thi_total ~ nm_factor_score + PTA_Better + core_total, data = nm_data)

summary(nm_scm_fsr)
```

```{r bayes scm nm factor score regression}
#nm_thesis unscaled model
nm_scm_factor_bayes_lm <- stan_glm(thi_total ~ core_total + nm_factor_score + PTA_Better, data = nm_data, seed = 12345)

#tidy and round model
tidy_nm_scm_factor_bayes_lm <- tidy(nm_scm_factor_bayes_lm) %>% 
  mutate_if(is.numeric, round, 3)

#nm_thesis scaled model
nm_scm_factor_bayes_lm_scaled <- stan_glm(thi_total_scaled ~ core_total_scaled+ scale(nm_factor_score) + PTA_Better_scaled, data = nm_data, seed = 12345)

#tidy and round model
tidy_nm_scm_factor_bayes_lm_scaled <- tidy(nm_scm_factor_bayes_lm_scaled) %>% 
  mutate_if(is.numeric, round, 3)

#draws from nm factor score model
nm_scm_factor_posterior_draws <- spread_draws(nm_scm_factor_bayes_lm, nm_factor_score, seed = 123)

nm_scm_factor_partial_beta_prob <- mean(nm_scm_factor_posterior_draws$nm_factor_score < 0) %>% round(digits = 2)
```

```{r EFiT principal axis factor analysis}
#create dateset to reduce
paf_efit_dat <- efit_scm %>%  select(nls_correct, matrixReason, keepTrack)

#sphericity
parameters::check_sphericity(paf_efit_dat)
KMO(paf_efit_dat)

#single factor no roation
efit_paf <- fa(paf_efit_dat, nfactors = 1, fm = "pa", rotate = 'none', covar = FALSE)
#stats
fa.stats(f = efit_paf)

#single factor no roation
#efit_fa_ml <- fa(paf_efit_dat, nfactors = 1, fm = "ml", rotate = 'oblimin', covar = FALSE)

fa.diagram(efit_paf)

fa.stats(f = efit_paf)
#single factor 

fa.parallel(paf_efit_dat, fa = "fa", fm = "pa")
#Thurstone is regression scores, cite skrondal 2001, Bartless methods gives the same lm inference
efit_fs <- factor.scores(paf_efit_dat, efit_paf, method = "Thurstone")

efit_factor_scores <- efit_fs$scores %>% unlist()
efit_factor_scores <- as.data.frame(efit_factor_scores)

efit_factor_scores <- efit_factor_scores$PA1

efit_scm <- cbind(efit_factor_scores, efit_scm)

efit_scm_fsr_lm <- lm(THI ~ efit_factor_scores + hearThresh + glo_psych, data = efit_scm)

summary(efit_scm_fsr_lm)
```

```{r bayes scm efit factor regression}
#efit unscaled model
efit_scm_factor_bayes_lm <- stan_glm(THI ~ glo_psych + efit_factor_scores + hearThresh, data = efit_scm, seed = 12345)

#tidy and round model
tidy_efit_scm_factor_bayes_lm <- tidy(efit_scm_factor_bayes_lm) %>% 
  mutate_if(is.numeric, round, 3)

#nm_thesis unscaled model
nm_scm_factor_bayes_lm <- stan_glm(thi_total ~ core_total + nm_factor_score + PTA_Better, data = nm_data, seed = 12345)

#tidy and round model
tidy_nm_scm_factor_bayes_lm <- tidy(nm_scm_factor_bayes_lm) %>% 
  mutate_if(is.numeric, round, 3)

#nm_thesis scaled model
nm_scm_factor_bayes_lm_scaled <- stan_glm(thi_total_scaled ~ core_total_scaled+ scale(nm_factor_score) + PTA_Better_scaled, data = nm_data, seed = 12345)

#tidy and round model
tidy_nm_scm_factor_bayes_lm_scaled <- tidy(nm_scm_factor_bayes_lm_scaled) %>% 
  mutate_if(is.numeric, round, 3)

#draws from efit factor score model
efit_scm_factor_posterior_draws <- spread_draws(efit_scm_factor_bayes_lm, efit_factor_scores, seed = 123)

efit_scm_factor_partial_beta_prob <- mean(efit_scm_factor_posterior_draws$efit_factor_scores < 0) %>% round(digits = 2)

#draws from nm factor score model
nm_scm_factor_posterior_draws <- spread_draws(nm_scm_factor_bayes_lm, nm_factor_score, seed = 123)

nm_scm_factor_partial_beta_prob <- mean(nm_scm_factor_posterior_draws$nm_factor_score < 0) %>% round(digits = 2)


```

##effect of tinnitus duration 
```{r prepare duration in each dataset and report removed missing}
efit_scm$TinDur <- as.numeric(efit_scm$TinDur)
#filter nas
efit_scm_tindur <- efit_scm %>% 
  filter(!is.na(TinDur))

nm_data$tin_dur <- as.numeric(nm_data$tin_dur)
#filter nas
nm_scm_tindur <- nm_data %>% 
  filter(!is.na(tin_dur))
```

```{r freq lm with tindur}
#efit
efit_scm_fsr_lm_dur <- lm(THI ~ efit_factor_scores + hearThresh + glo_psych + TinDur, data = efit_scm_tindur)

summary(efit_scm_fsr_lm_dur)
#nm
nm_scm_fsr_lm_dur <- lm(thi_total ~ nm_factor_score + PTA_Better + core_total + tin_dur, data = nm_scm_tindur)

summary(nm_scm_fsr_lm_dur)
```

```{r bayes lm with tindur}
#efit unscaled model
efit_scm_factor_bayes_lm_tindur <- stan_glm(THI ~ glo_psych + efit_factor_scores + TinDur + hearThresh, data = efit_scm_tindur, seed = 12345)

#tidy and round model
tidy_efit_scm_factor_bayes_lm_tindur <- tidy(efit_scm_factor_bayes_lm_tindur) %>% 
  mutate_if(is.numeric, round, 3)

#draws from efit factor score model with tindur
efit_scm_factor_posterior_draws_dur <- spread_draws(efit_scm_factor_bayes_lm_tindur, efit_factor_scores, seed = 123)

efit_scm_factor_partial_beta_prob_dur <- mean(efit_scm_factor_posterior_draws_dur$efit_factor_scores < 0) %>% round(digits = 2)

#nm_thesis unscaled model
nm_scm_factor_bayes_lm_dur <- stan_glm(thi_total ~ core_total + nm_factor_score + PTA_Better + tin_dur, data = nm_scm_tindur, seed = 12345)

#tidy and round model
tidy_nm_scm_factor_bayes_lm_dur <- tidy(nm_scm_factor_bayes_lm_dur) %>% 
  mutate_if(is.numeric, round, 3)

#draws from nm factor score model
nm_scm_factor_posterior_draws_dur <- spread_draws(nm_scm_factor_bayes_lm_dur, nm_factor_score, seed = 123)

nm_scm_factor_partial_beta_prob <- mean(nm_scm_factor_posterior_draws_dur$nm_factor_score < 0) %>% round(digits = 2)


```

